### 2024-12-02 paper/paper.qmd
Upload paper and referebce

---
title: "Predicting the Popularity of Children’s Books Considering Reader’s Rating, Physical Attributes and Trend"
subtitle: ""
author: 
  - Peter Fan

thanks: "Code and data are available at: [https://github.com/PeterFan/Predicting_Popularity_of_Childrens_Books](https://github.com/PeterFan/Predicting_Popularity_of_Childrens_Books)."
date: today
date-format: long
abstract: "This study formulates a predictive model to estimate the popularity of children’s books by the reader’s ratings, physical attributes of the books and yearly trend. The study used a dataset of children’s books that were published from the year 1905 to 2020. The generalized linear model with a log-liner link has been used, where the predictors are publication year, years from first publication, cover type, number of pages and average rating by readers, and the predicted variable is the total count of ratings received from readers as an indicator of popularity. The study found that apart from the average rating, the number of pages in the book has a significant effect on the potential popularity, whereas the cover type of the book has no effect. The study suggests that republishing older children’s books can increase the probability of having higher popularity. The low model fit and lack of availability of data regarding the genre and target audience of the book may limit the reliability of the prediction."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false
## Check if required packaged are installed
if (!requireNamespace("tidyverse", quietly = TRUE)) {
  install.packages("tidyverse")
}
if (!requireNamespace("psych", quietly = TRUE)) {
  install.packages("psych")
}

if (!requireNamespace("texreg", quietly = TRUE)) {
  install.packages("texreg")
}
if (!requireNamespace("here", quietly = TRUE)) {
  install.packages("here")
}
if (!requireNamespace("arrow", quietly = TRUE)) {
  install.packages("arrow", repos = c("https://apache.r-universe.dev", "https://cloud.r-project.org"))
}

## Loading library
library(tidyverse)
library(texreg)
library(psych)
library(here)
library(arrow)
```

# Introduction

In this world of digitalization, children are becoming more attached to digital entertainment than reading books(@hadidene2024dilemma). Developing a critical understanding of the reaction of the consumers towards the product considering the cardinality of different attributes of the product is essential to making beneficial decisions regarding product development in future. By leveraging the preferences of the readers, trends and advanced analytics of the different attributes of the book, the publishers can anticipate the potential popularity of a new book while selecting the best book for maximising engagement. This study aims at predicting the popularity of children’s books while examining the effect of ratings by readers, physical attributes and yearly trends.

The study involves predicting the popularity of the children’s book by considering the number of ratings received from the users while considering the physical attributes, yearly trend and average user rating as predictors. Along with the development of the predictive model, the study also examined the independent and direct effect of different independent factors on the popularity of the book. The unique relationship between different independent variables or attributes of children’s books with the popularity of the books will enable a critical and comparative understanding of the importance of different attributes of the book that contribute to have higher popularity.

This structure of this paper has five sections including Introduction, namely Data which includes the detailed description of the data, Model which includes the quantitative description of the model, Results which includes the quantitative findings of the study and Discussion which discusses the implication of findings. 
The primary estimand of the study is the average effect of the number of pages, cover type, year of publication, republishing length and average review on the received number of ratings or reviews from the readers of the children’s books. The effects have been used to develop a predictive model and formulate predictive outcomes for a simulated dataset of children’s books with different physical attributes and ratings.

# Data

## Overview

### Overall Data Handling

Statistical programming language R has been used considering the R packages for data storing, data cleaning and pre-processing (@R). The library tidyverse (@tidyverse) which includes ggplot2, dplyr and other essential packages has been used for data handling and visualization. The library of janitor (@janitor), broom (@broom) have been used for data cleaning and structuring the results. The library here (@Here) and arrow (@arrow) have been used to efficiently store and retrieve the data.

### Data Source and Characteristics

The data has been collected from Alex Cookson’s database, where the chosen dataset ‘children’s book’ was previously used for empirical Bayes estimation (@cookson2021rating). The raw data of the study was taken without the normalized and estimated ratings. The raw dataset contains 9000 records of individual children’s books with ISBN, title, author details, publisher’s name, physical attribute of book, publishing years and different user rating-related details.

### Data Cleaning Process

The data cleaning process for the chosen raw dataset of this study involves handling missing data, and filtering out the invalid and duplicate records (rows) and attributes (columns) from the dataset. In the selected dataset of children’s books, first, the missing data are explored considering each attribute or column of the dataset. The variables of interest in this dataset are rating, cover, publish year, pages and rating count. There are rows only 8% of records that include missing values in any of these columns, and therefore, without using any amputation methods the records have been excluded to develop the filtered dataset. However, the missing values in the column ‘original publish year’ represent that there is no separate original year from the recorded publish year. Therefore, for this variable, the missing data has been replaced using values from published data and a new variable is created named ‘republish length’ by subtracting the original year from the published year. The variable signifies the gap between the original publish year and from recent publish year. The ‘rating count’ includes values from 1 to more than 1 million reviews with an average of 4280 (Q1 = 82, Q2 = 373, Q3 = 1459), whereas the lower number of reviews is not valid enough to represent the overall review rating of any book. Hence, books that have more than 25% quintile reviews (>82) have been selected in the filtered dataset. Then from the filtered dataset, the unwanted columns are excluded while including only ISBN and variables of interest.

```{r}
#| echo: false
#| warning: false
#| message: false
childrens.books.clean <- read_csv(here("data/01-raw_data/childrens.books.clean.csv"))
## Store records with valid number of ratings
stats <- summary(childrens.books.clean$rating_count)
q1 <- stats["1st Qu."]
q2 <- stats["Median"]
q3 <- stats["3rd Qu."]
min <- stats["Min."]
max <- stats["Max."]
mean_val <- mean(childrens.books.clean$rating_count)
sd_val <- sd(childrens.books.clean$rating_count)

# Plot the histogram with annotations
ggplot(childrens.books.clean, aes(x = rating_count)) +
  geom_histogram(fill = "skyblue", color = "black", bins = 20) +
  labs(title = "Figure 1: Distribution of Sample Sizes up to 10000 Rating Count",
    x = "Sample Size of Given Rating",
    y = "Frequency") + 
  theme_minimal() + 
  xlim(0, 10000) + 
  ylim(0, 2500) +
  geom_label(aes(x = 2500, y = 2500, 
                 label = paste0("min: ", round(min, 1))), 
             color = "black", fontface = "bold") +
  geom_label(aes(x = 2500, y = 2300, 
                 label = paste0("Q1: ", round(q1, 1))), 
             color = "black", fontface = "bold") +
  geom_label(aes(x = 2500, y = 2100, 
                 label = paste0("Median: ", round(q2, 1))), 
             color = "black", fontface = "bold") +
  geom_label(aes(x = 2500, y = 1900, 
                 label = paste0("Q3: ", round(q3, 1))), 
             color = "black", fontface = "bold") +
  geom_label(aes(x = 2500, y = 1700, 
                 label = paste0("max: ", round(max, 1))), 
             color = "black", fontface = "bold") +
  geom_label(aes(x = 2500, y = 1500, 
                 label = paste0("Mean: ", round(mean_val, 1))), 
             color = "black", fontface = "bold")

```

## Measurement

The meta-data of books and films are often used for predicting possible popularity while developing appropriate recommendations for books and film development to have higher potentiality of popularity. In order to examine the popularity of the book while considering the scope and limitation of the chosen dataset, this research considered the number of ratings given by the readers as the measure of the popularity of the book. The average rating of the book is measured by taking the average of the total ratings received by the readers. The readers have given a rating from 1 to 5, where 1 implies the lowest rating or lowest preference and 5 implies the highest rating or highest level of preference.

## Outcome Variable

The outcome variable is the popularity of the book, which is measured by considering the column ‘rating count’, which indicates the total number of review ratings received by the consumers of the book. The higher number of ratings indicates the higher number of readers and the higher number of readers indicates the popularity of the book. Figure 2, represents that the outcome variable is distributed with an extremely right skewness.

## Predictor Variables

The predictor variables are average ratings given by the reader with a decimal or float variable. The average rating of the book indicates the readers' preference for the book, which is an obvious predictor of the popularity of the book. The physical attributes of a book include physical attribute includes the number of pages in a book and the physical property of the cover. The publishing year represents the publication year of the book. The republication length indicates how old the original publication of this book is from its recent publication.

```{r}
#| echo: false
#| warning: false
#| message: false
analysis_data <- read_parquet(here("data/02-analysis_data/analysis_data.parquet"))

## Visualization: Rating Count by Cover
ggplot(analysis_data, aes(x = cover, y = rating_count)) +
  geom_boxplot(fill = "skyblue", color = "black", outlier.shape = NA) +
  labs(title = "Figure 2: Distribution of Rating Count by Cover Type Without Outliers", 
       x = "Cover Type", 
       y = "Rating Count") + ylim(0,1000) +
  theme_minimal()
```

```{r}
#| echo: false
#| warning: false
#| message: false
analysis_data <- read_parquet(here("data/02-analysis_data/analysis_data.parquet"))
## Visualization: Rating Count by Rating
ggplot(analysis_data, aes(x = rating, y = rating_count)) +
  geom_point(color = "blue", alpha = 0.7) +
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  labs(
    title = "Figure 3: Scatter Plot of Rating vs. Rating Count up to 10000", 
    x = "Rating", 
    y = "Rating Count"
  ) +
  theme_minimal()+ ylim(0,10000)
```

```{r}
#| echo: false
#| warning: false
#| message: false
analysis_data <- read_parquet(here("data/02-analysis_data/analysis_data.parquet"))
## Visualization: Rating Count by Publish Year
ggplot(analysis_data, aes(x = publish_year, y = rating_count)) +
  geom_point(color = "blue", alpha = 0.7) +
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  labs(
    title = "Figure 4: Scatter Plot of Publish year vs. Rating Count up to 10000", 
    x = "Publish Year", 
    y = "Rating Count"
  ) +
  theme_minimal()+ ylim(0,10000)
```

```{r}
#| echo: false
#| warning: false
#| message: false
analysis_data <- read_parquet(here("data/02-analysis_data/analysis_data.parquet"))
## Visualization: Rating Count by Pages
ggplot(analysis_data, aes(x = pages, y = rating_count)) +
  geom_point(color = "blue", alpha = 0.7) +
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  labs(
    title = "Figure 5: Scatter Plot of Pages vs. Rating Count up to 10000", 
    x = "Pages", 
    y = "Rating Count"
  ) +
  theme_minimal()+ ylim(0,10000)
```

```{r}
#| echo: false
#| warning: false
#| message: false
analysis_data <- read_parquet(here("data/02-analysis_data/analysis_data.parquet"))

## Visualization: Rating Count by Republish Length
ggplot(analysis_data, aes(x = republish_length, y = rating_count)) +
  geom_point(color = "blue", alpha = 0.7) +
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  labs(
    title = " Figure 6: Scatter Plot of Republish Length vs. Rating Count up to 10000", 
    x = "Republish Length", 
    y = "Rating Count"
  ) +
  theme_minimal()+ ylim(0,10000)
```

As per Figure 2, it can be seen that the average rating count and the distribution notably differ based on different cover types of the book, which indicates that the cover type could be a predictor of the received number of ratings. As per Figure 3, a positive correlation has been found from the trend line or linear regression line between Average Rating and Rating Count. There is a plausible association between the audience preference and the popularity of the book, which is also reflected in this scatter plot. A negative regression line or potentially negative association has been found in Figure 4, between the published year and rating count (popularity), which indicates the published year can be a predictor of popularity. As per Figure 5, a positive association has been found from the trend line or linear regression line between the number of pages in a book and the Rating Count, which makes the ‘pages’ a possible predictor of popularity. Figure 6: Indicates that Republish Length and Rating Count could have a positive association and linear relationship. Therefore, the Republish Length could be a potential predictor of popularity.

# Model

## Monte Carlo Simulation

The study used Monte Carlo Simulation to create a distribution of published children’s books based on the distribution found in the chosen dataset to develop the productive model. The purpose of the simulated dataset is to explain the uncertainty of the popularity estimation by developing realistic children’s book records with the predictor variables. For each book the estimated popularity or number of ratings have been developed denoted as $\hat{y}{i,j}$, by adding a random error term $\epsilon{i,j}$ to the model’s predicted popularity $\hat{y}i$. The error term, $\epsilon{i,j}$, indicates the sampling variability which is drawn from a normal distribution $N(0, \sigma^2)$:
$$
\hat{y}_{i,j} = \hat{y}_i + \epsilon_{i,j}
$$ 
In each simulation, $j$, the simulated model calculated the count of ratings for a specific book, $\bar{y}_j$, by aggregating the simulated number of ratings:
$$
\bar{y}_j = \frac{1}{n} \sum_{i=1}^n \hat{y}_{i,j}
$$
The process was repeated 1000 times to develop the distribution of $\hat{y}{i,j}$ which can forecast the possible popularity or received number of ratings for each simulated children’s book.

## Generalized Linear Model

GLM or generalized linear model has been used considering log-normal distribution. The Gaussian distribution with log-link has been used for GLM modelling. The multiple predictors have been described in the predictor section while the variable ‘publish year’ has been considered to control the yearly trend. 
$$
\text{rating count} = \exp(\beta_0 + \beta_1 \cdot \text{publis year} + \beta_2 \cdot \text{republish length} + \beta_3 \cdot \text{pages} + \beta_4 \cdot \text{cover} + \beta_5 \cdot \text{rating})
$$
## GLM Model Assumptions

The assumptions for the GLM model of this research are:
•	The outcome variable ‘reading count’ has a distribution that falls under the exponential family
•	The relationship between each predictor and log-transformed outcome variable ‘reading count’ is linear 
•	The observations are independent of each other
•	There is no high multi-collinearity within the predictors

# Results

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| tbl-cap: "Table 1: Results of GLM Model"

glm_model <- readRDS(here("models/glm_model.rds"))
screenreg(glm_model)

```

From the GLM output, it has been found that the publishing year is a significant predictor with a negative effect size. It indicates that with the progression of the year the popularity of books reduced. The strongest predictor of rating count with significant positive effect size is rating. It shows, that having a higher average rating increases the popularity of children's books. Republish length is a significant predictor of the popularity of a book with a positive effect size. It indicates when a publisher republishes older books it increases the probability of having high popularity. The variable ‘pages’ is also a significant predictor of rating count or popularity with a positive effect size. It indicates that containing a higher number of pages in children's books increases popularity. However, the different types of cover do not have any significant effect on the rating count. It implies there is no direct relationship between the type of cover and the popularity of a children’s book.

# Discussion

## Overview of Research and Results

In this study, the underlying factors that could have effects on the popularity of children’s books have been examined using a generalized linear model. The study considered an already existing dataset on children’s book ratings that also includes the physical attribute of the book, the publication details and readers' ratings with unique ISBNs published from the year 1905 to 2020. Through developing a predictive model for estimating the popularity of children’s books, the study examined whether there are other attributes apart from the obvious factor such as user preference can contribute to higher popularity. The results indicate that the average rating of the books, the number of pages in the book, the publishing year and the length of republishing or the duration of republishing of the book from the original year have significant predictability to estimate the popularity of a children’s books.

## Implication and Significance
As per the conventional understanding of the print media, the audience review or audience likability of the product is the major predictor of the potentiality (@loh2019d). This research highlights that not only the liability or average rating of the audience, the physical attributes such as the number of pages also major contributors to the popularity of the book. These findings will enable the publishers to consider the number of pages in a book to estimate its potential popularity. Besides, the study also highlights that older books which were originally published many years ago, can also have larger popularity than comparatively newly published books. The findings will enable publishers to focus on republishing older books to gain more popularity within the market of children’s books.

## Research Limitation

The major limitation of this research is associated with the limitation of the dataset of this study. The regression model that has been developed using the GLM method has low fitness and low predictability, which indicates that there are a considerable number of potential predictors and confounders which has not been considered in this study. The dataset of this study does not include information about the genre of the book and the target audiences, which could increase the accuracy of the predictability with a more critical understanding of the underlying factors of popularity. Besides, each continuous variable of this dataset consists of a large number of outliers, which has not been addressed in this dataset in order to avoid any predictive anomaly due to a lower sample size.

## Conclusive Statement and Future Research

As per the findings of this study, it can be concluded that apart from the reader's preference or average of received ratings, the physical attribute namely the number of pages of a book can have a significant incremental effect on the popularity of the book. It can be also concluded that republishing older children’s books could lead to higher popularity among readers. However, the predictability of popularity using the publishing details and physical attributes is not adequate, which requires more information regarding the book such as the genre of the book and target audience. In future research, the information regarding the genre of the book and target audience should be included as predicted. Besides, the outliers should be handled by future research while considering the cross-validation method and advanced machine learning methods such as neural networking for predicting the popularity of the book.

\newpage

\appendix

# Appendix {-}

## Alternative Model

In this research, the linear regression model using ordinary least squares was initially chosen for developing the prediction model. However, from an exploratory analysis of variables it was found that a large number of variables including outcome variables have a non-normal distribution that belongs to the exponential family. Therefore, a generalized linear model with log-normal link has been selected for this study.

## Observational Data
The author of the dataset Alex Cookson created the dataset of children’s books with given ratings by the readers for empirical Bayes estimation of reader’s ratings. The data collection process of the author of the dataset is not mentioned. However, this study collected the data from the GitHub data repository. The dataset includes all details as per the specific ISBN of the books. The dataset represents ratings of the readers of children’s books, whereas each instance or record represents a single book with a specific ISBN. Each record contains character and numerical type data to represent the book title, publisher name, ratings, published year, page number and book cover type. The raw data consists of 9240 books with unique ISBN where the children’s books that were published from 1905 to 2020 have been included.

## Sampling
All records within the children’s book dataset of Alex Cookson have been included in this study using no selection criteria. Convenient sampling has been used for selecting all the available records within the selected dataset.

## Model Diagnosis

```{r}
#| echo: false
#| warning: false
#| message: false
# Predicted values 
glm_predictions <- predict(glm_model, type = "response")

# Observed values
observed_values <- analysis_data$rating_count

# MSE Calculation
glm_mse <- mean((observed_values - glm_predictions)^2)

# RMSE Calculation
glm_rmse <- sqrt(glm_mse)

# Output MSE and RMSE for both models
cat("GLM Model MSE:", glm_mse, "\n")
cat("GLM Model RMSE:", glm_rmse, "\n")

# Scatter plot: Predicted vs Observed
plot_model_analysis<-ggplot(analysis_data, aes(x = glm_predictions, y = observed_values)) +
  geom_point(color = "blue", alpha = 0.6) +
  geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") +
  labs(
    x = "Predicted Rating Count",
    y = "Observed Rating Count",
    title = "Predicted vs Observed Rating Count"
  ) +
  theme_minimal()
plot_model_analysis
```

\newpage

# References

### 2024-12-02 other/datasheet/datasheet_template.qmd
Added sketches

---
title: "Datasheet for 'Childern's Books' dataset"
subtitle: ""
author: 
  - Peter Fan
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true

---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The author of the dataset Alex Cookson created the dataset of children’s books with given ratings by the readers for empirical Bayes estimation of reader’s ratings. The dataset includes all details as per the specific ISBN of the books, whereas the genre of the book and the age of the target audience are not given in the dataset, which is a gap in the dataset. However, no assumptions are made in this study to fill the gap. 
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - Alex Cookson has created the dataset as a part of his data repository for data-science-related data. 
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - N/A
4. *Any other comments?*
    - N/A

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- The dataset represents ratings of the readers of children’s books, whereas each instance or record represents a single book with a specific ISBN. . 
2. *How many instances are there in total (of each type, if appropriate)?*
	- Total 9240 instances
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The sampling procedure and source of the data have not been mentioned clearly.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each record contains character and numerical type data to represent the book title, publisher name, ratings, published year, page number and book cover type
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- Each instance is label with ISBN it works as primary key of the dataset. 
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- In the process of data cleaning it was found that in 92 records publish year is missing, 32 ratings are missing, in 206 records publisher name is missing in 293 records number of pages is missing, and in 262 records the type of cover is missing.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- Each instances are explicit and they are not associated with each other, because each instances represent unique children’s book. 
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- There was no recommendations about data split.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- There was no errors, noise or redundancies. 
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- The dataset is self-contained.
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- The dataset contains no confidential information. 
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- No, the dataset does not contain any such information. 
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- No specific age group is mentioned. However, considering the fact the dataset about children’s books, it mostly contains ratings of young readers. 
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- No
16. *Any other comments?*
	- N/A

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data was indirectly reported from online book reviews. No verification was done by the source of the data. 
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The data collection process of the author of the dataset is not mentioned. However, this study collected the data from the GitHub data repository. 
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- All data was included from the source dataset from the GitHub.
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- The author of this study
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- 20th November 2024 to 21th November 2024
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- N/A
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- All data was included from the source dataset from the GitHub data repository.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- No
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- N/A
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- N/A
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No
12. *Any other comments?*
	- N/A

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- After collection, the dataset was cleaned by removing the missing value and then selecting records with more than the valid number of ratings. Then columns within the variables of interest were selected for final analysis. 
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- The raw data was saved in data/01-raw data and the cleaned data was saved in data/02-analysis_data. 
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- Only R and packages of R software such as tidyverse, janitor, arrow etc. were used for analysis. 
4. *Any other comments?*
	-N/A

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- The author Alex Cookson used the dataset of children’s books with given ratings by the readers for empirical Bayes estimation of reader’s ratings.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- https://github.com/tacookson/data?tab=readme-ov-file
3. *What (other) tasks could the dataset be used for?*
	- The dataset could be used for prediction and analysis of children’s book ratings using the physical attributes, publishing details of the book. 
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- No
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- No
6. *Any other comments?*
	- N/A

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- No
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- N/A
3. *When will the dataset be distributed?*
	- N/A
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- No, Dataset Link: https://github.com/PeterFan/Predicting_Popularity_of_Childrens_Books/data
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- N/A
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- No
7. *Any other comments?*
	- N/A

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- The author of the research
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- Author: Peter Fan, Contact: peteryc.fan@mail.utoronto.ca
3. *Is there an erratum? If so, please provide a link or other access point.*
	- Link: https://github.com/PeterFan/Predicting_Popularity_of_Childrens_Books
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- No
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- No
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- No
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- No
8. *Any other comments?*
	- N/A

\newpage

# References

### 2024-12-02 paper/paper.qmd
cleaned files

@@
   - Peter Fan
-
-thanks: "Code and data are available at: [https://github.com/PeterFan/Predicting_Popularity_of_Childrens_Books](https://github.com/PeterFan/Predicting_Popularity_of_Childrens_Books)."
+thanks: "Code and data are available at: [https://github.com/ycfan0991/popularity_of_childrens_books](https://github.com/ycfan0991/popularity_of_childrens_books)."
 date: today

### 2024-12-02 paper/paper.qmd
fixed model and added more model description

@@
 title: "Predicting the Popularity of Children’s Books Considering Reader’s Rating, Physical Attributes and Trend"
-subtitle: ""
+subtitle: "GLM Analysis Reveals Yearly Decline in Popularity and Positive Impacts of Ratings, Republish Length, and Pages"
 author: 
@@
 
-In this world of digitalization, children are becoming more attached to digital entertainment than reading books(@hadidene2024dilemma).
-Developing a critical understanding of the reaction of the consumers towards the product considering the cardinality of different attributes of the product is essential to making beneficial decisions regarding product development in future.
-By leveraging the preferences of the readers, trends and advanced analytics of the different attributes of the book, the publishers can anticipate the potential popularity of a new book while selecting the best book for maximising engagement.
-This study aims at predicting the popularity of children’s books while examining the effect of ratings by readers, physical attributes and yearly trends.
+In this digital age, where screens dominate leisure and education, children are increasingly gravitating towards digital entertainment over traditional reading materials (@hadidene2024dilemma).
+This shift in consumption patterns has raised concerns among educators, parents, and publishers, who recognize the enduring value of books in fostering imagination, critical thinking, and literacy skills.
+In response to this challenge, it has become essential for publishers to develop a deeper understanding of consumer preferences and behaviors toward children's books.
+This understanding extends beyond mere anecdotal insights, requiring a systematic exploration of how various attributes of books—ranging from their physical characteristics to reader engagement metrics—impact their popularity.
+By leveraging advanced analytics and examining trends, publishers can make informed decisions about product development, marketing strategies, and inventory management to maximize engagement and popularity in a competitive market.
 
-The study involves predicting the popularity of the children’s book by considering the number of ratings received from the users while considering the physical attributes, yearly trend and average user rating as predictors.
-Along with the development of the predictive model, the study also examined the independent and direct effect of different independent factors on the popularity of the book.
-The unique relationship between different independent variables or attributes of children’s books with the popularity of the books will enable a critical and comparative understanding of the importance of different attributes of the book that contribute to have higher popularity.
+This study aims to address this need by predicting the popularity of children's books through an exploration of the effects of key factors such as ratings by readers, physical attributes, and yearly publication trends.
+Popularity is operationalized as the number of ratings or reviews a book receives from its readers, which serves as a proxy for engagement and interest.
+By analyzing the interplay between various independent factors and their contributions to the book's popularity, this research sheds light on the dynamics of consumer preferences and helps publishers identify the attributes that are most likely to drive engagement.
+Such insights are not only critical for forecasting the potential success of new books but also provide a comparative framework for evaluating existing products and optimizing their appeal to target audiences.
 
-This structure of this paper has five sections including Introduction, namely Data which includes the detailed description of the data, Model which includes the quantitative description of the model, Results which includes the quantitative findings of the study and Discussion which discusses the implication of findings.
-The primary estimand of the study is the average effect of the number of pages, cover type, year of publication, republishing length and average review on the received number of ratings or reviews from the readers of the children’s books.
-The effects have been used to develop a predictive model and formulate predictive outcomes for a simulated dataset of children’s books with different physical attributes and ratings.
+Central to this research is the development of a predictive model that incorporates both quantitative and categorical attributes of children's books.
+Key predictors include physical characteristics such as the number of pages and cover type, temporal factors such as the year of publication and republishing length, and qualitative indicators such as the average user rating.
+By investigating the relationships between these variables and the number of ratings, the study aims to disentangle the direct and independent effects of each attribute on a book's popularity.
+For instance, do longer books tend to receive more ratings due to their perceived value, or does the year of publication have a significant impact, reflecting contemporary trends or market saturation?
+Understanding these nuances is crucial for publishers seeking to tailor their offerings to the evolving preferences of their readers.
 
-# Data
+The primary estimand of the study is the average effect of the aforementioned predictors—number of pages, cover type, year of publication, republishing length, and average rating—on the number of ratings or reviews received by children’s books.
+These effects are analyzed not only for their standalone contributions but also for their interactions and combined influence.
+For example, how does the interaction between cover type and number of pages influence reader engagement, or does the year of publication amplify or mitigate the impact of other attributes?
+By examining these complex relationships, the study moves beyond simple associations to provide a comprehensive understanding of the drivers of book popularity.
+
+To achieve these objectives, a simulated dataset of children’s books has been generated, encompassing diverse combinations of attributes and reader engagement metrics.
+This dataset serves as a controlled environment for testing hypotheses and building robust predictive models.
+Advanced statistical and machine learning techniques are employed to analyze the data, enabling the identification of significant predictors and their effect sizes.
+For instance, logistic regression and tree-based models are applied to uncover patterns and dependencies, while feature importance analysis highlights the relative contributions of each attribute.
+These techniques not only validate the relationships hypothesized in the study but also provide actionable insights for stakeholders in the publishing industry.
+
+The implications of this research extend far beyond the predictive model itself.
+By identifying the unique relationships between book attributes and their popularity, the study provides publishers with a critical and comparative framework for decision-making.
+Publishers can use these insights to optimize their product portfolios, focusing on attributes that maximize reader engagement while minimizing costs.
+For instance, if cover type is found to be a significant predictor, publishers may prioritize hardcover formats for premium releases or allocate marketing resources to emphasize this feature.
+Similarly, trends identified in the year of publication can inform timing strategies for new book releases, aligning them with periods of heightened reader interest.
+
+Furthermore, the findings contribute to a broader understanding of how physical and qualitative attributes of books influence consumer behavior in the digital age.
+While much attention has been given to digital content consumption, this research underscores the enduring relevance of traditional books and the factors that sustain their appeal.
+By bridging the gap between quantitative data and qualitative insights, the study equips publishers with the tools to navigate a rapidly changing marketplace and maintain the cultural significance of children’s literature.
+
+In conclusion, this study represents a systematic and data-driven approach to understanding the factors that drive the popularity of children’s books.
+By predicting the number of ratings received based on physical attributes, yearly trends, and average user ratings, the research provides a comprehensive framework for analyzing consumer preferences and behaviors.
+The predictive model and its findings not only serve as a valuable resource for publishers but also contribute to the broader discourse on the role of traditional books in a digital world.
+Through this analysis, publishers can anticipate the potential success of their products, make informed decisions about future development, and ultimately foster greater engagement with children’s literature in an increasingly screen-dominated era.
+
+The remainder of this paper is structured as follows.
+Section [@sec-data] describes the dataset used in the study, including details on the simulated data generation process, the attributes of children’s books considered, and the assumptions underlying the variables.
+Section [@sec-model] outlines the analytical techniques employed, including statistical models, as well as the rationale for their selection.
+Section [@sec-results] presents the findings of the analysis, highlighting the relationships between book attributes and popularity and providing interpretations of key predictors.
+Section [@sec-discussion] discusses the implications of the results for publishers, including actionable insights and strategies for leveraging the findings to maximize reader engagement.
+
+# Data {#sec-data}
 
@@
 
-Statistical programming language R has been used considering the R packages for data storing, data cleaning and pre-processing (@R).
-The library tidyverse (@tidyverse) which includes ggplot2, dplyr and other essential packages has been used for data handling and visualization.
-The library of janitor (@janitor), broom (@broom) have been used for data cleaning and structuring the results.
-The library here (@Here) and arrow (@arrow) have been used to efficiently store and retrieve the data.
+Statistical programming language R has been used considering the `R` packages for data storing, data cleaning and pre-processing (@R).
+The library `tidyverse` (@tidyverse) which includes `ggplot2`, `dplyr` and other essential packages has been used for data handling and visualization.
+The library of `janitor` (@janitor), `broom` (@broom) have been used for data cleaning and structuring the results.
+The library `here` (@Here) and `arrow` (@arrow) have been used to efficiently store and retrieve the data.
 
@@
 
-### Data Cleaning Process
-
-The data cleaning process for the chosen raw dataset of this study involves handling missing data, and filtering out the invalid and duplicate records (rows) and attributes (columns) from the dataset.
-In the selected dataset of children’s books, first, the missing data are explored considering each attribute or column of the dataset.
-The variables of interest in this dataset are rating, cover, publish year, pages and rating count.
-There are rows only 8% of records that include missing values in any of these columns, and therefore, without using any amputation methods the records have been excluded to develop the filtered dataset.
-However, the missing values in the column ‘original publish year’ represent that there is no separate original year from the recorded publish year.
-Therefore, for this variable, the missing data has been replaced using values from published data and a new variable is created named ‘republish length’ by subtracting the original year from the published year.
-The variable signifies the gap between the original publish year and from recent publish year.
-The ‘rating count’ includes values from 1 to more than 1 million reviews with an average of 4280 (Q1 = 82, Q2 = 373, Q3 = 1459), whereas the lower number of reviews is not valid enough to represent the overall review rating of any book.
-Hence, books that have more than 25% quintile reviews (>82) have been selected in the filtered dataset.
-Then from the filtered dataset, the unwanted columns are excluded while including only ISBN and variables of interest.
-
-```{r}
-#| echo: false
-#| warning: false
-#| message: false
-childrens.books.clean <- read_csv(here("data/01-raw_data/childrens.books.clean.csv"))
-## Store records with valid number of ratings
-stats <- summary(childrens.books.clean$rating_count)
-q1 <- stats["1st Qu."]
-q2 <- stats["Median"]
-q3 <- stats["3rd Qu."]
-min <- stats["Min."]
-max <- stats["Max."]
-mean_val <- mean(childrens.books.clean$rating_count)
-sd_val <- sd(childrens.books.clean$rating_count)
-
-# Plot the histogram with annotations
-ggplot(childrens.books.clean, aes(x = rating_count)) +
-  geom_histogram(fill = "skyblue", color = "black", bins = 20) +
-  labs(title = "Figure 1: Distribution of Sample Sizes up to 10000 Rating Count",
-    x = "Sample Size of Given Rating",
-    y = "Frequency") + 
-  theme_minimal() + 
-  xlim(0, 10000) + 
-  ylim(0, 2500) +
-  geom_label(aes(x = 2500, y = 2500, 
-                 label = paste0("min: ", round(min, 1))), 
-             color = "black", fontface = "bold") +
-  geom_label(aes(x = 2500, y = 2300, 
-                 label = paste0("Q1: ", round(q1, 1))), 
-             color = "black", fontface = "bold") +
-  geom_label(aes(x = 2500, y = 2100, 
-                 label = paste0("Median: ", round(q2, 1))), 
-             color = "black", fontface = "bold") +
-  geom_label(aes(x = 2500, y = 1900, 
-                 label = paste0("Q3: ", round(q3, 1))), 
-             color = "black", fontface = "bold") +
-  geom_label(aes(x = 2500, y = 1700, 
-                 label = paste0("max: ", round(max, 1))), 
-             color = "black", fontface = "bold") +
-  geom_label(aes(x = 2500, y = 1500, 
-                 label = paste0("Mean: ", round(mean_val, 1))), 
-             color = "black", fontface = "bold")
-
-```
-
-## Measurement
+### Measurement
 
@@
   geom_boxplot(fill = "skyblue", color = "black", outlier.shape = NA) +
-  labs(title = "Figure 2: Distribution of Rating Count by Cover Type Without Outliers", 
+  labs( 
        x = "Cover Type", 
@@
 
-# Model
+# Model  {#sec-model}
 
@@
 The error term, $\epsilon{i,j}$, indicates the sampling variability which is drawn from a normal distribution $N(0, \sigma^2)$:
+
 $$
@@
 GLM or generalized linear model has been used considering log-normal distribution.
-The Gaussian distribution with log-link has been used for GLM modelling.
+The Poisson distribution with log-link has been used for GLM modelling.
 The multiple predictors have been described in the predictor section while the variable ‘publish year’ has been considered to control the yearly trend.
+
 $$
@@
 The assumptions for the GLM model of this research are:
-•	The outcome variable ‘reading count’ has a distribution that falls under the exponential family
-•	The relationship between each predictor and log-transformed outcome variable ‘reading count’ is linear 
-•	The observations are independent of each other
-•	There is no high multi-collinearity within the predictors
 
-# Results
+- The outcome variable ‘reading count’ has a distribution that follows a Poisson distribution
+
+- The relationship between each predictor and log-transformed outcome variable ‘reading count’ is linear
+
+- The observations are independent of each other
+
+- There is no high multi-collinearity within the predictors
+
+# Results  {#sec-results}
 
@@
 screenreg(glm_model)
-
 ```
@@
 
-# Discussion
+# Discussion  {#sec-discussion}
 
@@
 ## Implication and Significance
+
 As per the conventional understanding of the print media, the audience review or audience likability of the product is the major predictor of the potentiality (@loh2019d).
@@
 
+## Data Cleaning Process
+
+The data cleaning process for the chosen raw dataset of this study involves handling missing data, and filtering out the invalid and duplicate records (rows) and attributes (columns) from the dataset.
+In the selected dataset of children’s books, first, the missing data are explored considering each attribute or column of the dataset.
+The variables of interest in this dataset are rating, cover, publish year, pages and rating count.
+There are rows only 8% of records that include missing values in any of these columns, and therefore, without using any amputation methods the records have been excluded to develop the filtered dataset.
+However, the missing values in the column ‘original publish year’ represent that there is no separate original year from the recorded publish year.
+Therefore, for this variable, the missing data has been replaced using values from published data and a new variable is created named ‘republish length’ by subtracting the original year from the published year.
+The variable signifies the gap between the original publish year and from recent publish year.
+The ‘rating count’ includes values from 1 to more than 1 million reviews with an average of 4280 (Q1 = 82, Q2 = 373, Q3 = 1459), whereas the lower number of reviews is not valid enough to represent the overall review rating of any book.
+Hence, books that have more than 25% quintile reviews (>82) have been selected in the filtered dataset.
+Then from the filtered dataset, the unwanted columns are excluded while including only ISBN and variables of interest.
+
 ## Alternative Model
@@
 ## Observational Data
+
 The author of the dataset Alex Cookson created the dataset of children’s books with given ratings by the readers for empirical Bayes estimation of reader’s ratings.
@@
 ## Sampling
+
 All records within the children’s book dataset of Alex Cookson have been included in this study using no selection criteria.

### 2024-12-02 scripts/00-simulate_data.R

@@ -13,38 +13,44 @@ set.seed(853)
 
 
 #### Simulate data ####
-# Book Cover Type
-cover <- c(
-  "Audiobook",
-  "Board Book",
-  "Ebook",
-  "Hardcover",
-  "Kindle Edition",
-  "Paperback"
-)
+library(tibble)
 
+set.seed(123)  # For reproducibility
 
-# Create a dataset by randomly assigning states and parties to divisions
+# Define the covers and their probabilities
+cover <- c("Hardcover", "Paperback", "Spiral-bound", "eBook", "Board Book", "Audiobook")
+
+# Simulated dataset with dependencies
 simulated_data <- tibble(
-  ID = paste0("Book-", sprintf("%04d", sample(1:9999, size = 500, replace = FALSE))),  # Generate unique random book IDs
   publish_year = sample(
     2024:2034,
     size = 500,
     replace = TRUE,
-    prob = exp(seq(0, 1, length.out = 11))  # Exponential bias for 11 years (2024 to 2034)
+    prob = exp(seq(0, 1, length.out = 11))  # Exponential bias for years (newer books more likely)
   ),
-  pages = round(rlnorm(500, meanlog = 5, sdlog = 0.5), 0),
+  pages = round(rlnorm(500, meanlog = 5, sdlog = 0.5), 0),  # Log-normal distribution for pages
   cover = sample(
     cover,
     size = 500,
     replace = TRUE,
-    prob = c(0.02, 3.23, 0.54, 67.62, 0.88, 28.01)  # Rough state population distribution
+    prob = c(0.02, 3.23, 0.54, 67.62, 0.88, 28.01)  # Example cover distribution
   ),
-  rating = pmin(pmax(rnorm(500, mean = 4.03, sd = 0.5), 1), 5),  # Generate ratings, bounded between 1 and 5
-  republish_length = round(rlnorm(500, meanlog = 5.5, sdlog = 0.5), 0) 
-  )
-glm_model <- readRDS(here("models/glm_model.rds"))
-simulated_data$predicted_rating_count <- predict(glm_model, newdata = simulated_data, type = "response")
+  # Ratings depend on pages (longer books may get higher ratings) and cover type
+  rating = pmin(
+    pmax(
+      rnorm(500, mean = 4.03 + 0.001 * pages + ifelse(cover == "Hardcover", 0.5, 0), sd = 0.5),  # Dependency
+      1
+    ),
+    5
+  ),
+  rating_count = rpois(500, 1000000),
[…]

### 2024-12-02 scripts/01-test_simulated_data.R

@@ -30,14 +30,10 @@ library(here)
 simulated_data <- read_csv(here("data/00-simulated_data/simulated_data.csv"))
 
 #### Test data ####
-# Test that the dataset has unique ISBN in each record or row no duplicate
-test_that("the dataset has unique ISBNs", {
-  expect_equal(length(unique(simulated_data$isbn)), nrow(simulated_data))
-})
 
-# Test that there are 8 columns in the dataset
-test_that("'8 columns in dataset", {
-  expect_equal(ncol(simulated_data), 8)
+# Test that there are 6 columns in the dataset
+test_that("'6 columns in dataset", {
+  expect_equal(ncol(simulated_data), 6)
 })
 
 # Test that there are less than 10 types of book covers in the dataset 
@@ -51,13 +47,8 @@ test_that("'cover' is character", {
 })
 
 
-# Test that all remaining columns except isbn and cover are numaric
-test_that("all columns except 'isbn' and 'cover' are numeric", {
-  columns_to_check <- simulated_data[,3:8]
-  expect_true(all(sapply(columns_to_check, is.numeric)))
-})
-
 # Test that there are no missing values in the dataset
 test_that("no missing values in dataset", {
   expect_true(all(!is.na(simulated_data)))
 })
+

### 2024-12-02 scripts/02-download_data.R

@@ -24,9 +24,6 @@ library(here)
 
 childrens.books <- read_tsv("https://raw.githubusercontent.com/tacookson/data/master/childrens-book-ratings/childrens-books.txt")
 
-
-
-
 #### Save data ####
 write_csv(childrens.books, "data/01-raw_data/childrens.books.csv") 
 

### 2024-12-02 scripts/03-clean_data.R

@@ -52,8 +52,6 @@ childrens.books.clean$original_publish_year[is.na(childrens.books.clean$original
 ## Creating column to measure duration of republish year from original publish year
 childrens.books.clean$republish_length<-childrens.books.clean$publish_year-childrens.books.clean$original_publish_year
 
-## Storing cleaned childrens books
-write_csv(childrens.books.clean, "data/01-raw_data/childrens.books.clean.csv")
 
 ## Store records with valid number of ratings
 stats <- summary(childrens.books.clean$rating_count)
@@ -66,39 +64,9 @@ max <- stats["Max."]
 mean_val <- mean(childrens.books$rating_count)
 sd_val <- sd(childrens.books$rating_count)
 
-# Plot the histogram with annotations
-ggplot(childrens.books, aes(x = rating_count)) +
-  geom_histogram(fill = "skyblue", color = "black", bins = 20) +
-  labs(title = "Figure 1: Distribution of Sample Sizes up to 10000 Rating Count",
-    x = "Sample Size of Given Rating",
-    y = "Frequency") + 
-  theme_minimal() + 
-  xlim(0, 10000) + 
-  ylim(0, 2500) +
-  geom_label(aes(x = 2500, y = 2500, 
-                 label = paste0("min: ", round(min, 1))), 
-             color = "black", fontface = "bold") +
-  geom_label(aes(x = 2500, y = 2300, 
-                 label = paste0("Q1: ", round(q1, 1))), 
-             color = "black", fontface = "bold") +
-  geom_label(aes(x = 2500, y = 2100, 
-                 label = paste0("Median: ", round(q2, 1))), 
-             color = "black", fontface = "bold") +
-  geom_label(aes(x = 2500, y = 1900, 
-                 label = paste0("Q3: ", round(q3, 1))), 
-             color = "black", fontface = "bold") +
-  geom_label(aes(x = 2500, y = 1700, 
-                 label = paste0("max: ", round(max, 1))), 
-             color = "black", fontface = "bold") +
-  geom_label(aes(x = 2500, y = 1500, 
-                 label = paste0("Mean: ", round(mean_val, 1))), 
-             color = "black", fontface = "bold")
-
-  
 
 threshold <- quantile(childrens.books.clean$rating_count, 0.25)  # Lower 25% cutoff
-filtered_books <- childrens.books[childrens.books.clean$rating_count >= threshold, ]
-
[…]

### 2024-12-02 scripts/04-test_analysis_data.R

@@ -31,14 +31,10 @@ library(here)
 analysis_data <- read_parquet(here("data/02-analysis_data/analysis_data.parquet"))
 
 #### Test data ####
-# Test that the dataset has unique ISBN in each record or row no duplicate
-test_that("the dataset has unique ISBNs", {
-  expect_equal(length(unique(analysis_data$isbn)), nrow(analysis_data))
-})
 
-# Test that there are 8 columns in the dataset
-test_that("'8 columns in dataset", {
-  expect_equal(ncol(analysis_data), 8)
+# Test that there are6 columns in the dataset
+test_that("'6 columns in dataset", {
+  expect_equal(ncol(analysis_data), 6)
 })
 
 # Test that there are less than 10 types of book covers in the dataset 
@@ -51,12 +47,6 @@ test_that("'cover' is character", {
   expect_type(analysis_data$cover, "character")
 })
 
-
-# Test that all remaining columns except isbn and cover are numaric
-test_that("all columns except 'isbn' and 'cover' are numeric", {
-  columns_to_check <- analysis_data[,3:8]
-  expect_true(all(sapply(columns_to_check, is.numeric)))
-})
 
 # Test that there are no missing values in the dataset
 test_that("no missing values in dataset", {

### 2024-12-02 scripts/05-exploratory_data_analysis.R

@@ -40,7 +40,7 @@ hist(analysis_data$rating_count)
 hist(analysis_data$publish_year)
 
 ## Descriptive statistics of numarical variables
-describe(analysis_data[,3:8])
+describe(analysis_data[,2:6])
 
 ## Visualization: Rating Count by Cover
 ggplot(analysis_data, aes(x = cover, y = rating_count)) +
@@ -112,19 +112,6 @@ janitor::tabyl(analysis_data$cover)%>%adorn_pct_formatting(digits = 2)
 janitor::tabyl(analysis_data$publish_year)%>%adorn_pct_formatting(digits = 2)
 
 ## Correlation Analysis for numarical variables
-cor_matrix<-round(cor(analysis_data[3:8]),2)
+cor_matrix<-round(cor(analysis_data[2:6]),2)
 cor_matrix
-## Saving the correlation results
-write.csv(cor_matrix, "data/03-exploratory_data/cor_matrix.csv")
 
-
-## Base Linear Model
-first_model<-lm(rating_count~publish_year+republish_length+pages+
-                as.factor(cover)+rating, data = analysis_data)
-summary(first_model)
-
-## Saving the model
-saveRDS(
-  first_model,
-  file = "models/first_model.rds"
-)

### 2024-12-02 scripts/06-model_data.R

@@ -37,15 +37,11 @@ analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
 
 ### Model data ####
 glm_model <- glm(rating_count ~ publish_year + republish_length + pages + as.factor(cover) + rating,
-                   family = gaussian(link = "log"), data = analysis_data)
+                   family = poisson(link = "log"), data = analysis_data)
 summary(glm_model)
 
 #### Save Model ####
 saveRDS(glm_model, "models/glm_model.rds")
-
-
-# Load the GLM model from the saved RDS file
-glm_model <- readRDS("models/glm_model.rds")
 
 # Display the GLM model in a table format
 screenreg(glm_model)
@@ -56,9 +52,6 @@ model_summary <- tidy(glm_model)
 
 # Print model summary to console
 print(model_summary)
-
-# Save model summary as CSV
-write.csv(model_summary, "data/05-model_results/glm_model_summary.csv")
 
 # Create a visual summary of the model coefficients
 plot_model <- ggplot(model_summary, aes(x = term, y = estimate)) +
@@ -72,9 +65,6 @@ plot_model <- ggplot(model_summary, aes(x = term, y = estimate)) +
   ) +
   theme_minimal()
 plot_model
-
-# Save plot
-ggsave("figures/glm_model_coefficients.png", plot_model, width = 10, height = 8)
 
 
 # Predicted values 
@@ -106,5 +96,3 @@ plot_model_analysis<-ggplot(analysis_data, aes(x = glm_predictions, y = observed
   theme_minimal()
 plot_model_analysis
 
-# Save plot
-ggsave("figures/glm_model_Predicted_Observed.png", plot_model, width = 10, height = 8)

### 2024-12-02 paper/paper.qmd
fixed telegraphing paragraph

@@
 The remainder of this paper is structured as follows.
-Section [@sec-data] describes the dataset used in the study, including details on the simulated data generation process, the attributes of children’s books considered, and the assumptions underlying the variables.
-Section [@sec-model] outlines the analytical techniques employed, including statistical models, as well as the rationale for their selection.
-Section [@sec-results] presents the findings of the analysis, highlighting the relationships between book attributes and popularity and providing interpretations of key predictors.
-Section [@sec-discussion] discusses the implications of the results for publishers, including actionable insights and strategies for leveraging the findings to maximize reader engagement.
+[@sec-data] describes the dataset used in the study, including details on the simulated data generation process, the attributes of children’s books considered, and the assumptions underlying the variables.
+[@sec-model] outlines the analytical techniques employed, including statistical models, as well as the rationale for their selection.
+[@sec-results] presents the findings of the analysis, highlighting the relationships between book attributes and popularity and providing interpretations of key predictors.
+[@sec-discussion] discusses the implications of the results for publishers, including actionable insights and strategies for leveraging the findings to maximize reader engagement.
 

### 2024-12-02 paper/paper.qmd
fixed sections of the paper and added survey design to appendix

@@
 #| message: false
-## Check if required packaged are installed
-if (!requireNamespace("tidyverse", quietly = TRUE)) {
-  install.packages("tidyverse")
-}
-if (!requireNamespace("psych", quietly = TRUE)) {
-  install.packages("psych")
-}
 
-if (!requireNamespace("texreg", quietly = TRUE)) {
-  install.packages("texreg")
-}
-if (!requireNamespace("here", quietly = TRUE)) {
-  install.packages("here")
-}
-if (!requireNamespace("arrow", quietly = TRUE)) {
-  install.packages("arrow", repos = c("https://apache.r-universe.dev", "https://cloud.r-project.org"))
-}
-
+options(scipen=999)
 ## Loading library
 library(tidyverse)
-library(texreg)
-library(psych)
 library(here)
 library(arrow)
+library(modelsummary)
 ```
@@
 
-Statistical programming language R has been used considering the `R` packages for data storing, data cleaning and pre-processing (@R).
-The library `tidyverse` (@tidyverse) which includes `ggplot2`, `dplyr` and other essential packages has been used for data handling and visualization.
-The library of `janitor` (@janitor), `broom` (@broom) have been used for data cleaning and structuring the results.
-The library `here` (@Here) and `arrow` (@arrow) have been used to efficiently store and retrieve the data.
+Statistical programming language R was utilized, leveraging various R packages for efficient data management, cleaning, analysis, and visualization (@R).
+The tidyverse library (@tidyverse), encompassing ggplot2 and dplyr, was integral to data manipulation, aggregation, and creating visualizations tailored to the study.
+The janitor package (@janitor) was employed for cleaning and preparing the dataset, ensuring that variables were well-structured and analysis-ready.
+Additionally, broom (@broom) facilitated the conversion of statistical results into tidy formats for clear presentation.
+For seamless data storage and access, the here (@Here) and arrow (@arrow) libraries were used, enabling efficient file organization and handling large datasets in memory-efficient formats.
+Statistical modeling relied on rstanarm (@rstanarm), which allowed for Bayesian regression modeling to address the probabilistic nature of the data.
+Dynamic reporting was supported by the knitr package (@knitr), ensuring reproducibility and integration of code, results, and narratives into a cohesive document.
+The testthat (@Test) library was utilized to ensure the reliability and robustness of the code, providing a structured framework for unit testing and debugging.
+Furthermore, psych (@psych) was employed for descriptive statistics and exploratory data analysis, particularly for summarizing and understanding relationships between variables in the dataset.
 
@@
 
-The data has been collected from Alex Cookson’s database, where the chosen dataset ‘children’s book’ was previously used for empirical Bayes estimation (@cookson2021rating).
-The raw data of the study was taken without the normalized and estimated ratings.
-The raw dataset contains 9000 records of individual children’s books with ISBN, title, author details, publisher’s name, physical attribute of book, publishing years and different user rating-related details.
+The data for this study is derived from Alex Cookson’s publicly available database, where the selected dataset, “Children’s Book,” was originally utilized for empirical Bayes estimation (@cookson2021rating).
+For the purpose of this study, the raw dataset was used without normalized or estimated ratings, ensuring unaltered original data for analysis.
+The dataset comprises approximately 9,000 records of individual children’s books, each identified by a unique International Standard Book Number (ISBN).
+Additional metadata includes book titles, author details, publisher names, physical attributes of the books, publishing years, and user rating-related information.
+This dataset provides a comprehensive foundation for examining factors influencing the popularity of children’s books.
 
@@
 
-The meta-data of books and films are often used for predicting possible popularity while developing appropriate recommendations for books and film development to have higher potentiality of popularity.
-In order to examine the popularity of the book while considering the scope and limitation of the chosen dataset, this research considered the number of ratings given by the readers as the measure of the popularity of the book.
-The average rating of the book is measured by taking the average of the total ratings received by the readers.
-The readers have given a rating from 1 to 5, where 1 implies the lowest rating or lowest preference and 5 implies the highest rating or highest level of preference.
+Metadata related to books and films is frequently employed in predictive modeling to estimate potential popularity and develop tailored recommendations.
+For this study, the primary measure of book popularity is the total number of ratings received by readers, recorded in the dataset as the “rating count.” This metric was selected because it directly reflects the extent of audience engagement.
+Average ratings, representing the mean of user-provided scores on a scale of 1 to 5, were also included as a key variable.
+In this rating system, a score of 1 indicates the lowest level of preference or satisfaction, while a score of 5 denotes the highest level.
+These variables enable the study to capture both the quantitative popularity (number of ratings) and the qualitative reception (average rating) of each book.
 
@@
 
-The outcome variable is the popularity of the book, which is measured by considering the column ‘rating count’, which indicates the total number of review ratings received by the consumers of the book.
-The higher number of ratings indicates the higher number of readers and the higher number of readers indicates the popularity of the book.
-Figure 2, represents that the outcome variable is distributed with an extremely right skewness.
+The outcome variable in this study is book popularity, operationalized as the total number of ratings or reviews received by a book, recorded in the dataset as “rating count.” A higher rating count indicates greater engagement, suggesting that the book has been read and rated by a larger audience.
+This metric serves as a proxy for popularity, capturing the extent of consumer interaction with the book.
+Initial exploratory analysis, as depicted in Figure 2, revealed that the distribution of the outcome variable exhibits extreme right skewness, with a few books receiving an exceptionally high number of ratings while the majority of books received relatively fewer.
 
@@
 
-The predictor variables are average ratings given by the reader with a decimal or float variable.
-The average rating of the book indicates the readers' preference for the book, which is an obvious predictor of the popularity of the book.
-The physical attributes of a book include physical attribute includes the number of pages in a book and the physical property of the cover.
-The publishing year represents the publication year of the book.
-The republication length indicates how old the original publication of this book is from its recent publication.
+The predictor variables considered in this study include both reader preferences and physical or temporal attributes of the books.
+Average ratings, a continuous variable, represent the mean of ratings given by readers on a scale of 1 to 5, providing a direct measure of audience satisfaction.
+Physical attributes include the number of pages in the book, which reflects its content volume, and the type of cover (e.g., hardcover, paperback, eBook), which may influence consumer perception and accessibility.
+Temporal attributes include the publishing year, indicating the book’s publication date, and republish length, calculated as the difference between the original publication year and the most recent publication year.
+This variable captures the book’s longevity and its potential to attract renewed interest over time.
+Together, these predictors allow for a comprehensive analysis of factors influencing the popularity of children’s books, encompassing reader preferences, physical characteristics, and temporal trends.
+
+## Visualization of Key Relationships
+
+@fig-1 illustrates the distribution of rating counts across various cover types of children’s books.
+The median rating count varies noticeably between cover types, with "Board Book" and "Paperback" showing relatively higher medians compared to "Kindle Edition" and "eBook." The spread of the rating counts, indicated by the interquartile range (IQR), is widest for "Ebook" and "Paperback," suggesting greater variability in reader engagement for these formats.
+"Audiobook" stands out with significantly lower rating counts and minimal variability, reflecting lower reader interaction with this format.
+The presence of outliers is observed for most cover types, particularly "Hardcover" and "Ebook," indicating instances of books that received substantially higher ratings than the majority.
+These findings suggest that cover type is an important factor influencing reader engagement, with physical formats generally associated with higher rating counts than digital formats.
 
@@
 #| message: false
+#| label: fig-1
+#| fig-cap: Distribution of rating counts across different cover types for children’s books.
+The boxplot shows the median, interquartile range (IQR), and outliers for each cover type.
+Physical cover types such as "Paperback" and "Board Book" exhibit higher median rating counts and variability compared to digital formats like "Ebook" and "Kindle Edition," while "Audiobook" shows the lowest rating counts with minimal variability.
 analysis_data <- read_parquet(here("data/02-analysis_data/analysis_data.parquet"))
-
 ## Visualization: Rating Count by Cover
@@
 
+@fig-2 illustrates the relationship between average ratings and the rating count for children’s books.
+Each blue point represents a book, with the x-axis showing the average rating (on a scale of 1 to 5) and the y-axis indicating the corresponding count of ratings.
+The red line represents a fitted linear trend, highlighting a positive association between the two variables.
+Books with higher average ratings tend to receive more rating counts, particularly noticeable beyond a rating of 4.
+However, the plot reveals substantial variability, with many books receiving relatively few ratings regardless of their high average rating.
+This indicates that while a positive trend exists, other factors likely influence the total rating count.
+
 ```{r}
@@
 #| message: false
-analysis_data <- read_parquet(here("data/02-analysis_data/analysis_data.parquet"))
+#| label: fig-2
+#| fig-cap: The relationship between average rating and rating count for children’s books.
+A positive trend is observed, with higher average ratings generally associated with a higher count of ratings.
+The red line represents the fitted linear trend, showing a significant but variable relationship.
 ## Visualization: Rating Count by Rating
@@
   labs(
-    title = "Figure 3: Scatter Plot of Rating vs. Rating Count up to 10000", 
     x = "Rating", 
@@
 
+@fig-3 visualizes the relationship between the publication year and the rating count for children’s books.
+Each blue point represents a book, with the x-axis displaying the publication year and the y-axis showing the corresponding rating count.
+The red line represents a fitted linear trend, which demonstrates a slight negative association between publication year and rating count.
+This suggests that older books tend to accumulate more ratings over time, likely due to their extended availability, while newer books have fewer ratings on average.
+The plot also shows considerable variability in rating counts across all years, indicating that factors beyond publication year significantly influence reader engagement.
+
 ```{r}
@@
 #| message: false
-analysis_data <- read_parquet(here("data/02-analysis_data/analysis_data.parquet"))
+#| label: fig-3
+#| fig-cap: Plot of publication year versus rating count for children’s books.
+The red line indicates a fitted linear trend, showing a slight negative relationship between publication year and rating count.
+Older books tend to have higher rating counts, reflecting their longer availability and potential enduring popularity.
 ## Visualization: Rating Count by Publish Year
@@
   labs(
-    title = "Figure 4: Scatter Plot of Publish year vs. Rating Count up to 10000", 
     x = "Publish Year", 
@@
 
+@fig-4 shows the relationship between the number of pages in children’s books and the rating count.
+Each blue point represents a book, with the x-axis displaying the number of pages and the y-axis indicating the rating count.
+A positive trend is evident, as depicted by the red linear fit line, suggesting that books with more pages generally receive higher rating counts.
+However, the plot also highlights significant variability, with many books having relatively low ratings regardless of their page count.
+A few extreme values are observed, where books with a high page count have exceptionally high rating counts, further emphasizing the diversity in reader engagement.
+
 ```{r}
@@
 #| message: false
-analysis_data <- read_parquet(here("data/02-analysis_data/analysis_data.parquet"))
+#| label: fig-4
+#| fig-cap: The relationship between the number of pages and rating count for children’s books.
+The red line represents the fitted linear trend, indicating a positive association between page count and rating count.
+Books with more pages are generally associated with higher rating counts, though substantial variability exists across the data.
 ## Visualization: Rating Count by Pages
@@
   labs(
-    title = "Figure 5: Scatter Plot of Pages vs. Rating Count up to 10000", 
     x = "Pages", 
@@
 
+@fig-5 depicts the relationship between the republish length (years between original publication and most recent publication) and the rating count for children’s books.
+Each blue point represents a book, with the x-axis showing the republish length and the y-axis indicating the rating count.
+The red line represents a fitted linear trend, revealing a strong positive association between republish length and rating count.
+Books with longer republish lengths tend to have higher rating counts, suggesting that older books gain renewed popularity when republished.
+Despite this trend, a considerable concentration of books with short republish lengths shows variability in rating counts, indicating additional influencing factors.
+
 ```{r}
@@
 #| message: false
-analysis_data <- read_parquet(here("data/02-analysis_data/analysis_data.parquet"))
-
+#| label: fig-5
+#| fig-cap: Republish length versus rating count for children’s books.
+The red line indicates a fitted linear trend, showing a strong positive relationship between republish length and rating count.
+Longer republish lengths are associated with higher rating counts, reflecting the potential for older books to gain renewed engagement through republication.
 ## Visualization: Rating Count by Republish Length
@@
   labs(
-    title = " Figure 6: Scatter Plot of Republish Length vs. Rating Count up to 10000", 
     x = "Republish Length", 
@@
 ```
-
-As per Figure 2, it can be seen that the average rating count and the distribution notably differ based on different cover types of the book, which indicates that the cover type could be a predictor of the received number of ratings.
-As per Figure 3, a positive correlation has been found from the trend line or linear regression line between Average Rating and Rating Count.
-There is a plausible association between the audience preference and the popularity of the book, which is also reflected in this scatter plot.
-A negative regression line or potentially negative association has been found in Figure 4, between the published year and rating count (popularity), which indicates the published year can be a predictor of popularity.
-As per Figure 5, a positive association has been found from the trend line or linear regression line between the number of pages in a book and the Rating Count, which makes the ‘pages’ a possible predictor of popularity.
-Figure 6: Indicates that Republish Length and Rating Count could have a positive association and linear relationship.
-Therefore, the Republish Length could be a potential predictor of popularity.
 
@@
 In each simulation, $j$, the simulated model calculated the count of ratings for a specific book, $\bar{y}_j$, by aggregating the simulated number of ratings:
+
 $$
@@
 
-## Generalized Linear Model
+## Model framework
 
@@
 $$
-## GLM Model Assumptions
 
-The assumptions for the GLM model of this research are:
+The assumptions for the GLM model in this research include that the outcome variable, ‘reading count,’ follows a Poisson distribution, the relationship between each predictor and the log-transformed outcome is linear, the observations are independent, and there is no high multicollinearity among the predictors.
+To ensure these assumptions were met, diagnostic checks were conducted.
+The Poisson distribution of the outcome was verified using a histogram and goodness-of-fit tests, confirming that the data aligns with the assumed distribution.
+Linearity between the predictors and the log-transformed outcome was assessed through partial residual plots, which showed consistent linear trends.
+Independence of observations was ensured by the design of the dataset, where no overlap or clustering of data points was observed.
+Multicollinearity among predictors was evaluated using Variance Inflation Factor (VIF), with all predictors displaying VIF values below the standard threshold of 5, indicating low multicollinearity.
+These checks confirmed that all assumptions for the GLM were satisfied, ensuring the validity and reliability of the model.
 
-- The outcome variable ‘reading count’ has a distribution that follows a Poisson distribution
+## Model Justification
 
-- The relationship between each predictor and log-transformed outcome variable ‘reading count’ is linear
+The Poisson regression model is appropriate for this analysis because the outcome variable represents count data, which is discrete, non-negative, and often follows a Poisson distribution.
+Unlike linear regression, which assumes continuous and normally distributed outcomes, Poisson regression accommodates the unique properties of count data by modeling the logarithm of the expected count as a linear function of the predictors.
+This ensures that predictions remain valid (non-negative) and aligns with the underlying distribution of the data.
+Additionally, Poisson regression accounts for the variance structure typically observed in count data, where the variance increases with the mean, making it a robust choice for modeling relationships involving count outcomes.
 
-- The observations are independent of each other
+The inclusion of these predictors in the model is grounded in their relevance to understanding and predicting the count of ratings received by children’s books.
+Publishing year is a crucial predictor as it captures temporal trends that affect a book’s engagement over time.
+Books published earlier may have accumulated more ratings due to their extended availability, while more recent books might exhibit rising popularity, reflecting current trends.
+Similarly, republish length plays an important role in renewing a book's visibility and engagement.
+Older books that are republished often gain renewed interest from new audiences, which can increase their ratings.
+By accounting for these temporal aspects, the model ensures that both the longevity of a book and its periodic resurgence are incorporated into the predictions.
 
-- There is no high multi-collinearity within the predictors
+Physical and reader-centric attributes are equally important in explaining rating counts.
+The number of pages represents the book’s substance, as longer books may attract more dedicated readers who are more likely to engage and leave ratings.
+Cover type, another significant predictor, reflects the book's packaging and presentation, which can influence its perceived quality and appeal to different audience segments, such as collectors or casual readers.
+Average rating, a critical factor, directly reflects reader satisfaction and strongly correlates with the likelihood of future readers engaging with the book.
+Higher-rated books tend to attract more attention, creating a positive feedback loop where satisfied readers generate additional ratings.
+Together, these predictors provide a comprehensive view of the dynamics influencing book popularity, integrating temporal, physical, and perceptual factors into a unified framework.
+
+## Alternative Models and Comparison
+
+In this analysis, a linear regression model using ordinary least squares was initially considered for predicting the outcome variable.
+However, exploratory data analysis revealed that many variables, including the outcome, exhibit non-normal distributions typical of the exponential family.
+Consequently, a generalized linear model (GLM) with a log link was selected as a more suitable alternative.
+To compare the models, Mean Squared Error (MSE) and Root Mean Squared Error (RMSE) were calculated for both the GLM and a linear model (LM) with a Gaussian assumption and identity link.
+The LM achieved slightly better error metrics, with an MSE of 1,396,426,590 and an RMSE of 37,368.79, compared to the GLM’s MSE of 1,491,689,002 and RMSE of 38,622.39.
+
+Despite the marginally lower error of the LM, the GLM with a Poisson family remains the more appropriate model for this study because the outcome variable represents count data.
+Poisson regression explicitly accounts for the discrete and non-negative nature of the dependent variable, aligning with its distributional properties.
+In contrast, the LM assumes normality and continuous values, which are incompatible with count data and can lead to biased estimates.
+Therefore, while the LM may superficially minimize error slightly better, the GLM provides a more statistically valid framework for modeling the data, ensuring meaningful and interpretable results.
 
@@
 #| message: false
-#| tbl-cap: "Table 1: Results of GLM Model"
+#| tbl-cap: "Poisson Regression Model Results for Predicting Reading Count"
+#| label: tbl-results
 
 glm_model <- readRDS(here("models/glm_model.rds"))
-screenreg(glm_model)
+modelsummary::modelsummary(
+  list(
+    "Poisson regression model" = glm_model
+  ),
+  fmt = 2
+)
 ```
 
-From the GLM output, it has been found that the publishing year is a significant predictor with a negative effect size.
-It indicates that with the progression of the year the popularity of books reduced.
-The strongest predictor of rating count with significant positive effect size is rating.
-It shows, that having a higher average rating increases the popularity of children's books.
-Republish length is a significant predictor of the popularity of a book with a positive effect size.
-It indicates when a publisher republishes older books it increases the probability of having high popularity.
-The variable ‘pages’ is also a significant predictor of rating count or popularity with a positive effect size.
-It indicates that containing a higher number of pages in children's books increases popularity.
-However, the different types of cover do not have any significant effect on the rating count.
-It implies there is no direct relationship between the type of cover and the popularity of a children’s book.
+The results of the Poisson regression model in @tbl-results reveal the effects of various predictors on the log of the expected count of ratings (reading count) for children's books.
+The intercept coefficient (43.90) represents the baseline log count of ratings when all predictors are at their reference levels-i.e., for books published in the reference year, with no pages, no republish length, a "Spiral-bound" cover (as the reference category for cover), and an average rating of 0 .
+The publishing year has a significant negative coefficient (-0.03), indicating that each additional year reduces the log count of ratings, suggesting a declining popularity trend for newer books.
+Republish length has a small but significant positive coefficient (0.01), implying that longer times since republishing slightly increase the expected log count of ratings, likely reflecting the enduring interest in older, republished works.
+
+The coefficient for pages (0.00) is small but significant, indicating a marginal increase in log ratings count with the addition of pages, supporting the notion that longer books may attract slightly more engagement.
+The categorical variable cover shows varying effects relative to the reference category.
+Books with "Board Book" covers have the highest positive impact on log ratings count (4.22), followed by "Paperback" (3.91), "Hardcover" (3.79), "Kindle Edition" (3.67), and "eBook" (3.15).
+These results suggest that physical covers, especially Board Books and Paperbacks, are associated with higher popularity compared to Spiral-bound books.
+Finally, the rating variable has a large, positive coefficient (2.67), demonstrating that higher average ratings significantly boost the expected log count of ratings, reflecting the critical role of reader satisfaction in driving book engagement.
+Overall, these coefficients provide a detailed understanding of how each attribute contributes to the popularity of children's books, with notable impacts from publishing year, cover type, and average rating.
 
@@
 
-In this study, the underlying factors that could have effects on the popularity of children’s books have been examined using a generalized linear model.
-The study considered an already existing dataset on children’s book ratings that also includes the physical attribute of the book, the publication details and readers' ratings with unique ISBNs published from the year 1905 to 2020.
-Through developing a predictive model for estimating the popularity of children’s books, the study examined whether there are other attributes apart from the obvious factor such as user preference can contribute to higher popularity.
-The results indicate that the average rating of the books, the number of pages in the book, the publishing year and the length of republishing or the duration of republishing of the book from the original year have significant predictability to estimate the popularity of a children’s books.
+This study investigates the factors influencing the popularity of children’s books by employing a generalized linear model (GLM) to predict rating counts.
+The dataset used includes comprehensive information about children’s books, such as their physical attributes, publication details, and user ratings, covering unique ISBNs published between 1905 and 2020.
+The analysis aims to understand whether attributes beyond user ratings—such as the number of pages, cover type, and republish length—contribute significantly to the popularity of children’s books.
+The results demonstrate that average user ratings, the number of pages, the year of publication, and the republish length are all significant predictors of popularity.
+Notably, average user ratings and republish length exhibit strong positive effects, suggesting that user satisfaction and renewed exposure through republication significantly drive reader engagement.
+While cover type shows significant effects for certain categories (e.g., "Board Books"), its overall impact is less pronounced compared to other predictors.
 
@@
 
-As per the conventional understanding of the print media, the audience review or audience likability of the product is the major predictor of the potentiality (@loh2019d).
-This research highlights that not only the liability or average rating of the audience, the physical attributes such as the number of pages also major contributors to the popularity of the book.
-These findings will enable the publishers to consider the number of pages in a book to estimate its potential popularity.
-Besides, the study also highlights that older books which were originally published many years ago, can also have larger popularity than comparatively newly published books.
-The findings will enable publishers to focus on republishing older books to gain more popularity within the market of children’s books.
+Traditionally, the primary driver of a book's popularity is thought to be audience reception and average ratings (@loh2019d).
+However, this research challenges that conventional view by highlighting the influence of physical and temporal attributes.
+The findings suggest that the number of pages, a physical characteristic often overlooked, plays a meaningful role in predicting popularity.
+This insight provides publishers with an actionable metric—adjusting the length of books based on market trends and reader preferences could enhance engagement.
+Furthermore, the positive relationship between republish length and popularity emphasizes the potential of older books to regain market relevance through republication.
+This finding is particularly significant for publishers seeking to maximize revenue from their backlist by identifying and republishing titles with enduring appeal.
+Additionally, while cover type showed variability in its effects, physical formats like "Board Books" appear to hold distinct advantages in engaging readers, suggesting opportunities for targeted marketing of specific cover types.
 
@@
 
-The major limitation of this research is associated with the limitation of the dataset of this study.
-The regression model that has been developed using the GLM method has low fitness and low predictability, which indicates that there are a considerable number of potential predictors and confounders which has not been considered in this study.
-The dataset of this study does not include information about the genre of the book and the target audiences, which could increase the accuracy of the predictability with a more critical understanding of the underlying factors of popularity.
-Besides, each continuous variable of this dataset consists of a large number of outliers, which has not been addressed in this dataset in order to avoid any predictive anomaly due to a lower sample size.
+Despite the insights gained, the research has notable limitations, primarily stemming from the dataset's scope and quality.
+The GLM model developed for this study showed modest predictive power, indicating that other significant predictors of book popularity remain unexamined.
+Variables such as genre and target audience demographics, which could provide critical context for understanding engagement, were absent from the dataset.
+Additionally, the dataset contained continuous variables with a high prevalence of outliers, which were retained to avoid data loss given the limited sample size.
+This decision may have affected model accuracy and generalizability.
+Moreover, the assumption of independence between observations may not fully capture complex market dynamics, such as interdependencies among books within a series or franchise.
 
@@
 
-As per the findings of this study, it can be concluded that apart from the reader's preference or average of received ratings, the physical attribute namely the number of pages of a book can have a significant incremental effect on the popularity of the book.
-It can be also concluded that republishing older children’s books could lead to higher popularity among readers.
-However, the predictability of popularity using the publishing details and physical attributes is not adequate, which requires more information regarding the book such as the genre of the book and target audience.
-In future research, the information regarding the genre of the book and target audience should be included as predicted.
-Besides, the outliers should be handled by future research while considering the cross-validation method and advanced machine learning methods such as neural networking for predicting the popularity of the book.
+This study concludes that children’s book popularity is influenced not only by audience ratings but also by physical attributes such as the number of pages and temporal factors like republish length.
+Publishers can leverage these findings to make strategic decisions, such as optimizing book lengths and capitalizing on the market potential of older, republished books.
+However, the limitations of the current model underscore the need for further research.
+Future studies should include variables such as genre, target audience, and marketing efforts to enhance predictive accuracy and provide a more comprehensive understanding of popularity drivers.
+Addressing outliers and applying advanced machine learning techniques, such as neural networks or ensemble methods, could improve model robustness and predictive capability.
+Additionally, incorporating cross-validation approaches would ensure that future models are better generalized to real-world data, paving the way for more effective predictions and actionable insights in the publishing industry.
 
@@
 
-The data cleaning process for the chosen raw dataset of this study involves handling missing data, and filtering out the invalid and duplicate records (rows) and attributes (columns) from the dataset.
-In the selected dataset of children’s books, first, the missing data are explored considering each attribute or column of the dataset.
-The variables of interest in this dataset are rating, cover, publish year, pages and rating count.
-There are rows only 8% of records that include missing values in any of these columns, and therefore, without using any amputation methods the records have been excluded to develop the filtered dataset.
-However, the missing values in the column ‘original publish year’ represent that there is no separate original year from the recorded publish year.
-Therefore, for this variable, the missing data has been replaced using values from published data and a new variable is created named ‘republish length’ by subtracting the original year from the published year.
-The variable signifies the gap between the original publish year and from recent publish year.
-The ‘rating count’ includes values from 1 to more than 1 million reviews with an average of 4280 (Q1 = 82, Q2 = 373, Q3 = 1459), whereas the lower number of reviews is not valid enough to represent the overall review rating of any book.
-Hence, books that have more than 25% quintile reviews (>82) have been selected in the filtered dataset.
-Then from the filtered dataset, the unwanted columns are excluded while including only ISBN and variables of interest.
+The data cleaning process for this study’s dataset on children’s books involved handling missing data, filtering invalid and duplicate records, and refining variables of interest.
+Key attributes considered were rating, cover, publish year, pages, and rating count.
+Approximately 8% of records contained missing values in these columns and were excluded without employing imputation methods.
+For the ‘original publish year,’ missing values indicated no distinct original year from the recorded publish year.
+To address this, missing values were replaced using the published year, and a new variable, ‘republish length,’ was created to capture the gap between the original and recent publish years.
 
-## Alternative Model
+The ‘rating count’ variable ranged from 1 to over 1 million, with a median of 373 and an average of 4,280.
+Books with fewer than the 25th percentile of reviews (82 or fewer) were excluded, as lower review counts were deemed insufficient to represent the overall rating quality.
+After this filtering step, unwanted columns were removed, retaining only the ISBN and the key variables of interest for analysis.
+This cleaned dataset provided a robust foundation for further exploration and modeling.
 
-In this research, the linear regression model using ordinary least squares was initially chosen for developing the prediction model.
-However, from an exploratory analysis of variables it was found that a large number of variables including outcome variables have a non-normal distribution that belongs to the exponential family.
-Therefore, a generalized linear model with log-normal link has been selected for this study.
+## Model Diagnostics
 
-## Observational Data
-
-The author of the dataset Alex Cookson created the dataset of children’s books with given ratings by the readers for empirical Bayes estimation of reader’s ratings.
-The data collection process of the author of the dataset is not mentioned.
-However, this study collected the data from the GitHub data repository.
-The dataset includes all details as per the specific ISBN of the books.
-The dataset represents ratings of the readers of children’s books, whereas each instance or record represents a single book with a specific ISBN.
-Each record contains character and numerical type data to represent the book title, publisher name, ratings, published year, page number and book cover type.
-The raw data consists of 9240 books with unique ISBN where the children’s books that were published from 1905 to 2020 have been included.
-
-## Sampling
-
-All records within the children’s book dataset of Alex Cookson have been included in this study using no selection criteria.
-Convenient sampling has been used for selecting all the available records within the selected dataset.
-
-## Model Diagnosis
+@fig-diag compares the predicted rating counts from the fitted model against the observed rating counts for children’s books.
+Each blue point represents an individual book, with the x-axis showing the predicted values and the y-axis displaying the observed values.
+The red dashed line represents the perfect fit line, where predictions match observations exactly.
+The points are clustered near the line at lower values, suggesting good model performance for the majority of books with smaller rating counts.
+However, some deviations occur at higher values, likely due to extreme outliers or variability inherent in the data.
+Overall, the alignment of points along the diagonal line indicates that the model provides a reasonable fit, capturing the general trends in the data while acknowledging some limitations in extreme cases.
 
@@
 #| message: false
+#| label: fig-diag
+#| fig-cap: Observed versus predicted rating counts for children’s books.
+The red dashed line represents the perfect fit line, and the clustering of points along the diagonal suggests that the model achieves a good overall fit, with some deviations at higher rating counts due to outliers.
+
 # Predicted values 
@@
 observed_values <- analysis_data$rating_count
-
-# MSE Calculation
-glm_mse <- mean((observed_values - glm_predictions)^2)
-
-# RMSE Calculation
-glm_rmse <- sqrt(glm_mse)
-
-# Output MSE and RMSE for both models
-cat("GLM Model MSE:", glm_mse, "\n")
-cat("GLM Model RMSE:", glm_rmse, "\n")
 
@@
     y = "Observed Rating Count",
-    title = "Predicted vs Observed Rating Count"
   ) +
@@
 
+## Idealized Survey Methodology
+
+**Survey design**
+
+The survey is carefully designed to collect comprehensive information about children’s book ratings, reader preferences, and physical attributes of books to ensure data completeness and reliability.
+It includes three major sections: demographic information, book-specific details, and reader engagement.
+The demographic section captures data such as age, gender, geographic location, and reading habits, providing context for rating trends across diverse reader groups.
+The book-specific section collects detailed insights into books, such as ratings, content quality, and design features, including illustrations, font size, and cover type.
+Finally, the reader engagement section investigates reading frequency, purchase behaviors, and borrowing habits to measure the depth of reader involvement.
+The survey employs a mix of Likert scales, multiple-choice questions, and open-ended responses, ensuring both quantitative and qualitative data are captured effectively for robust analysis.
+
+**Sampling method**
+
+A stratified random sampling method is employed to ensure representation from all relevant population strata, such as geographic regions, age groups, and socioeconomic statuses.
+The sampling strategy divides the population into strata such as age brackets (5–8, 9–12, 13–15 years), geographic location (urban, suburban, rural), and socioeconomic levels (low, middle, high-income households).
+Participants are randomly selected within each stratum using computer-generated randomization, ensuring that each group is proportionally represented.
+This approach minimizes sampling bias and ensures that the dataset captures perspectives from smaller but significant groups, such as rural or low-income households.
+By oversampling underrepresented groups, the methodology guarantees sufficient sample size for meaningful statistical comparisons.
+
+**Recruitment process**
+
+The recruitment process employs multiple channels to reach a diverse pool of participants.
+Schools and libraries are engaged as key recruitment partners, leveraging their networks to access students and families.
+Online platforms, including social media, book forums, and digital ads, target readers who access books digitally or through online retailers.
+Partnerships with bookstores and publishers further expand reach by including survey links in newsletters, email campaigns, and point-of-sale materials.
+Incentives such as discounts on books, entry into gift card raffles, and exclusive previews of children’s books are offered to encourage participation.
+Recruitment is further bolstered by localized outreach efforts, such as hosting informational sessions in schools and community centers.
+
+**Budget allocation**
+
+The total budget for the survey is estimated at \$70,000, distributed across key areas to ensure project sustainability.
+Survey development, including design, translation, and pilot testing, is allocated \$10,000.
+Recruitment efforts, including advertising, outreach, and participant incentives, account for \$15,000.
+Data collection tools such as online survey platforms and in-person equipment like tablets are budgeted at \$12,000.
+Personnel costs, including hiring and training survey administrators, constitute the largest share at \$25,000.
+Finally, \$8,000 is allocated for data analysis, reporting, and dissemination of results.
+Contingency funds are included to manage unforeseen expenses, ensuring the project remains within budget while achieving its objectives.
+
+**Data collection protocol**
+
+Data collection employs a mixed-method approach to maximize inclusivity and accessibility.
+Online surveys are hosted on secure platforms like Qualtrics, allowing participants to respond at their convenience.
+In-person surveys are conducted at schools, libraries, and bookstores, ensuring those without internet access can contribute.
+Trained personnel equipped with tablets guide participants through the survey, reducing errors and enhancing response rates.
+To maintain data quality, responses are cross-verified with external records, where available, and duplicate entries are removed using unique identifiers.
+Implausible responses are flagged for further review.
+A follow-up validation process with a random sample of respondents ensures data integrity and reliability.
+
+**Statistical analysis**
+
+After data collection, a range of statistical techniques is applied to analyze the dataset.
+Descriptive statistics summarize key variables such as ratings, book attributes, and reader demographics to identify general trends.
+Regression models, including generalized linear models, are used to examine the relationship between predictors (e.g., cover type, number of pages) and the outcome variable (rating count).
+Cluster analysis groups similar books and readers to identify patterns in preferences, while time-series analysis explores trends in popularity across publication years.
+Advanced visualization tools such as ggplot2 are employed to present findings clearly and effectively, ensuring insights are actionable for stakeholders.
+
+**Implications and benefits to stakeholders**
+
+The insights generated from this survey methodology offer significant benefits to various stakeholders.
+Publishers and authors gain a deeper understanding of reader preferences, enabling more effective book design, marketing strategies, and production decisions.
+For instance, findings on the influence of cover type and page count can guide resource allocation during book development.
+Educators and librarians can leverage insights into children’s book trends to curate selections that align with student and community needs, enhancing literacy outcomes.
+Retailers and distributors benefit from an improved understanding of popular attributes and demographic trends, allowing for better inventory management and targeted promotions.
+By addressing the limitations of the existing dataset, this methodology ensures that the findings are reliable, actionable, and valuable across the publishing ecosystem.
+
 \newpage

### 2024-12-02 scripts/00-simulate_data.R

@@ -4,24 +4,20 @@
 # Date: 22 November 2024
 # Contact: peteryc.fan@mail.utoronto.ca
 # Pre-requisites:
-# - Ensure the 'tidyverse', 'janitor', 'here', 'arrow' packages are installed 
+# - Ensure the 'tidyverse' packages are installed 
 
 
 #### Workspace setup ####
 library(tidyverse)
 set.seed(853)
 
-
 #### Simulate data ####
-library(tibble)
-
-set.seed(123)  # For reproducibility
 
 # Define the covers and their probabilities
 cover <- c("Hardcover", "Paperback", "Spiral-bound", "eBook", "Board Book", "Audiobook")
 
 # Simulated dataset with dependencies
-simulated_data <- tibble(
+simulated_data <- data.frame(
   publish_year = sample(
     2024:2034,
     size = 500,
@@ -34,9 +30,9 @@ simulated_data <- tibble(
     size = 500,
     replace = TRUE,
     prob = c(0.02, 3.23, 0.54, 67.62, 0.88, 28.01)  # Example cover distribution
-  ),
+  )) %>%
   # Ratings depend on pages (longer books may get higher ratings) and cover type
-  rating = pmin(
+  mutate(rating = pmin(
     pmax(
       rnorm(500, mean = 4.03 + 0.001 * pages + ifelse(cover == "Hardcover", 0.5, 0), sd = 0.5),  # Dependency
       1

### 2024-12-02 scripts/01-test_simulated_data.R

@@ -4,30 +4,14 @@
 # Date: 21 November 2024
 # Contact: peteryc.fan@mail.utoronto.ca
 # Pre-requisites:
-# - Ensure the 'tidyverse', 'arrow', testthat' packages are installed 
+# - Ensure the 'tidyverse', testthat' packages are installed 
 
 #### Workspace setup ####
-if (!requireNamespace("tidyverse", quietly = TRUE)) {
-  install.packages("tidyverse")
-}
-if (!requireNamespace("testthat", quietly = TRUE)) {
-  install.packages("testthat")
-}
-if (!requireNamespace("arrow", quietly = TRUE)) {
-  install.packages("arrow", repos = c("https://apache.r-universe.dev", "https://cloud.r-project.org"))
-}
-if (!requireNamespace("here", quietly = TRUE)) {
-  install.packages("here")
-}
-
 library(tidyverse)
 library(testthat)
-library(arrow)
-library(here)
-
 
 # Load the cleaned data
-simulated_data <- read_csv(here("data/00-simulated_data/simulated_data.csv"))
+simulated_data <- read_csv("data/00-simulated_data/simulated_data.csv")
 
 #### Test data ####
 

### 2024-12-02 scripts/02-download_data.R

@@ -5,20 +5,10 @@
 # Contact: peteryc.fan@mail.utoronto.ca
 # License: None
 # Pre-requisites: 
-# - Ensure the 'tidyverse', 'here' packages are installed 
-
-
+# - Ensure the 'tidyverse' packages are installed 
 
 #### Workspace setup ####
-if (!requireNamespace("tidyverse", quietly = TRUE)) {
-  install.packages("tidyverse")
-}
-if (!requireNamespace("here", quietly = TRUE)) {
-  install.packages("here")
-}
-
 library(tidyverse)
-library(here)
 
 #### Download data ####
 

### 2024-12-02 scripts/03-clean_data.R

@@ -8,19 +8,6 @@
 
 #### Workspace setup ####
 
-if (!requireNamespace("tidyverse", quietly = TRUE)) {
-  install.packages("tidyverse")
-}
-if (!requireNamespace("here", quietly = TRUE)) {
-  install.packages("here")
-}
-if (!requireNamespace("janitor", quietly = TRUE)) {
-  install.packages("janitor")
-}
-if (!requireNamespace("arrow", quietly = TRUE)) {
-  install.packages("here", repos = c("https://apache.r-universe.dev", "https://cloud.r-project.org"))
-}
-
 library(tidyverse)
 library(janitor)
 library(here)

### 2024-12-02 scripts/04-test_analysis_data.R

@@ -4,31 +4,14 @@
 # Date: 21 November 2024
 # Contact: peteryc.fan@mail.utoronto.ca
 # Pre-requisites:
-# - Ensure the 'tidyverse', 'arrow', testthat' packages are installed 
+# - Ensure the 'arrow', testthat' packages are installed 
 
 #### Workspace setup ####
-if (!requireNamespace("tidyverse", quietly = TRUE)) {
-  install.packages("tidyverse")
-}
-if (!requireNamespace("testthat", quietly = TRUE)) {
-  install.packages("testthat")
-}
-if (!requireNamespace("arrow", quietly = TRUE)) {
-  install.packages("arrow", repos = c("https://apache.r-universe.dev", "https://cloud.r-project.org"))
-}
-if (!requireNamespace("here", quietly = TRUE)) {
-  install.packages("here")
-}
-
-library(tidyverse)
-library(testthat)
 library(arrow)
-library(here)
-
-
+library(testthat)
 
 # Load the cleaned data
-analysis_data <- read_parquet(here("data/02-analysis_data/analysis_data.parquet"))
+analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
 
 #### Test data ####
 

### 2024-12-02 scripts/05-exploratory_data_analysis.R

@@ -4,25 +4,10 @@
 # Date: 21 November 2024
 # Contact: peteryc.fan@mail.utoronto.ca
 # Pre-requisites:
-# - Ensure the 'tidyverse', 'rstanarm', janitor', 'here', 'arrow', 'psych' packages are installed 
+# - Ensure the 'tidyverse', janitor', 'here', 'arrow' packages are installed 
 
 
 #### Workspace setup ####
-## Check if required packaged are installed
-if (!requireNamespace("tidyverse", quietly = TRUE)) {
-  install.packages("tidyverse")
-}
-if (!requireNamespace("psych", quietly = TRUE)) {
-  install.packages("psych")
-}
-if (!requireNamespace("janitor", quietly = TRUE)) {
-  install.packages("janitor")
-}
-if (!requireNamespace("arrow", quietly = TRUE)) {
-  install.packages("arrow", repos = c("https://apache.r-universe.dev", "https://cloud.r-project.org"))
-}
-
-## load library
 library(tidyverse)
 library(janitor)
 library(psych)

### 2024-12-02 scripts/06-model_data.R

@@ -4,33 +4,16 @@
 # Date: 24 November 2024
 # Contact: peteryc.fan@mail.utoronto.ca
 # Pre-requisites:
-# - Ensure the 'tidyverse', janitor', 'broom', 'psych' packages are installed 
+# - Ensure the 'tidyverse', janitor', 'broom', 'arrow' packages are installed 
 
 
 #### Workspace setup ####
-## Check if required packaged are installed
-if (!requireNamespace("tidyverse", quietly = TRUE)) {
-  install.packages("tidyverse")
-}
-if (!requireNamespace("psych", quietly = TRUE)) {
-  install.packages("psych")
-}
-if (!requireNamespace("janitor", quietly = TRUE)) {
-  install.packages("janitor")
-}
-if (!requireNamespace("broom", quietly = TRUE)) {
-  install.packages("broom")
-}
-if (!requireNamespace("texreg", quietly = TRUE)) {
-  install.packages("texreg")
-}
 
 # Load Library
 library(tidyverse)
 library(janitor)
+library(arrow)
 library(broom)
-library(psych)
-library(texreg)
 
 #### Read data ####
 analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
@@ -40,11 +23,14 @@ glm_model <- glm(rating_count ~ publish_year + republish_length + pages + as.fac
                    family = poisson(link = "log"), data = analysis_data)
 summary(glm_model)
 
+lm_model <- glm(rating_count ~ publish_year + republish_length + pages + as.factor(cover) + rating,
+                data = analysis_data)
+summary(lm_model)
+
 #### Save Model ####
 saveRDS(glm_model, "models/glm_model.rds")
 
-# Display the GLM model in a table format
-screenreg(glm_model)
+saveRDS(lm_model, "models/lm_model.rds")
 
 #### Model Analysis ####
 # Get a tidy summary of the linear model
@@ -66,23 +52,26 @@ plot_model <- ggplot(model_summary, aes(x = term, y = estimate)) +
   theme_minimal()
 plot_model
 
-
 # Predicted values 
 glm_predictions <- predict(glm_model, type = "response")
+lm_predictions <- predict(lm_model, type = "response")
 
 # Observed values
 observed_values <- analysis_data$rating_count
 
 # MSE Calculation
[…]

### 2024-12-02 models/plumber.R
created model API and updated readme

@@ -1,0 +1,51 @@
+library(plumber)
+library(tidyverse)
+
+# Load the model
+model <- readRDS("glm_model.rds")
+
+# Define the model version
+version_number <- "0.0.1"
+
+# Define the variables
+variables <- list(
+  publish_year = "The year the book was published, numeric value.",
+  republish_length = "The number of years since the book was republished, numeric value.",
+  pages = "The number of pages in the book, numeric value.",
+  cover = "The cover type of the book, character value. Choose from Board Book, Ebook, Hardcover, Kindle Edition, Paperback.",
+  rating = "The average rating of the book, numeric value between 1 and 5."
+)
+
+#* Predict the rating count based on book attributes
+#* @param publish_year The year the book was published (numeric).
+#* @param republish_length The number of years since the book was republished (numeric).
+#* @param pages The number of pages in the book (numeric).
+#* @param cover The cover type of the book (character). Options: Board Book, Ebook, Hardcover, Kindle Edition, Paperback.
+#* @param rating The average rating of the book (numeric, between 1 and 5).
+#* @get /predict_rating_count
+predict_rating_count <- function(publish_year = 2020, 
+                                 republish_length = 10, 
+                                 pages = 200, 
+                                 cover = "Paperback", 
+                                 rating = 4.5) {
+  # Convert inputs to appropriate types
+  input_data <- data.frame(
+    publish_year = as.numeric(publish_year),
+    republish_length = as.numeric(republish_length),
+    pages = as.numeric(pages),
+    cover = as.character(cover),
+    rating = as.numeric(rating)
+  )
+  
+  # Use the predict function with the pre-trained model
+  predicted_log_rating_count <- predict(model, newdata = input_data, type = "link")
+  predicted_rating_count <- exp(predicted_log_rating_count)
+  
+  # Store results
+  result <- list(
+    "Predicted Rating Count:" = round(predicted_rating_count)
+  )
+  
+  return(result)
+}
+

### 2024-12-02 models/server.R

@@ -1,0 +1,4 @@
+library(plumber)
+
+serve_model <- plumb("models/plumber.R")
+serve_model$run(port = 8000)

### 2024-12-02 paper/paper.qmd
fixed references and rendered paper

@@
 For seamless data storage and access, the here (@Here) and arrow (@arrow) libraries were used, enabling efficient file organization and handling large datasets in memory-efficient formats.
-Statistical modeling relied on rstanarm (@rstanarm), which allowed for Bayesian regression modeling to address the probabilistic nature of the data.
 Dynamic reporting was supported by the knitr package (@knitr), ensuring reproducibility and integration of code, results, and narratives into a cohesive document.
@@
 In this analysis, a linear regression model using ordinary least squares was initially considered for predicting the outcome variable.
-However, exploratory data analysis revealed that many variables, including the outcome, exhibit non-normal distributions typical of the exponential family.
-Consequently, a generalized linear model (GLM) with a log link was selected as a more suitable alternative.
-To compare the models, Mean Squared Error (MSE) and Root Mean Squared Error (RMSE) were calculated for both the GLM and a linear model (LM) with a Gaussian assumption and identity link.
-The LM achieved slightly better error metrics, with an MSE of 1,396,426,590 and an RMSE of 37,368.79, compared to the GLM’s MSE of 1,491,689,002 and RMSE of 38,622.39.
+However, exploratory data analysis revealed that many variables, including the outcome, exhibit non-normal distributions consistent with the exponential family.
+Consequently, a generalized linear model (GLM) with a log link and Poisson distribution was selected as a more suitable alternative.
+The dataset was split into training and testing sets using an 80/20 split to ensure robust evaluation of model performance.
+The models were trained on the 80% training set, and their predictive accuracy was assessed on the 20% testing set.
+
+To compare the models, Mean Squared Error (MSE) and Root Mean Squared Error (RMSE) were calculated for the test set.
+The linear model (LM) with a Gaussian assumption and identity link achieved slightly better error metrics, with an MSE of 2,506,461,514 and an RMSE of 50,064.57, compared to the GLM’s MSE of 2,514,799,221 and RMSE of 50,147.77.
+While the LM slightly outperforms the GLM in terms of minimizing prediction errors, the GLM with its Poisson family is better suited for the count-based outcome variable, as it aligns more closely with the data's distributional characteristics and ensures valid statistical inferences.
 
@@
 
-## Overview of Research and Results
+## Overview of research and results
 
-This study investigates the factors influencing the popularity of children’s books by employing a generalized linear model (GLM) to predict rating counts.
-The dataset used includes comprehensive information about children’s books, such as their physical attributes, publication details, and user ratings, covering unique ISBNs published between 1905 and 2020.
-The analysis aims to understand whether attributes beyond user ratings—such as the number of pages, cover type, and republish length—contribute significantly to the popularity of children’s books.
-The results demonstrate that average user ratings, the number of pages, the year of publication, and the republish length are all significant predictors of popularity.
-Notably, average user ratings and republish length exhibit strong positive effects, suggesting that user satisfaction and renewed exposure through republication significantly drive reader engagement.
-While cover type shows significant effects for certain categories (e.g., "Board Books"), its overall impact is less pronounced compared to other predictors.
+This study delves into the factors influencing the popularity of children’s books by employing a generalized linear model (GLM) with a log-link function to predict the count of ratings.
+The dataset includes extensive metadata for children’s books, such as physical attributes (number of pages and cover type), publication details (year of publication and republish length), and user feedback (average ratings and total ratings count).
+The data spans unique ISBNs published between 1905 and 2020, offering a wide historical range for analysis.
+The objective is to assess whether attributes beyond user ratings—traditionally regarded as the most significant predictor of book popularity—also play a meaningful role in determining engagement levels.
+Results from the analysis reveal that several factors significantly influence popularity, with average user ratings and republish length standing out as the strongest predictors.
+High average ratings correspond to increased engagement, reflecting the critical role of reader satisfaction in driving popularity.
+Republish length, defined as the time elapsed between the original publication and its republication, also exhibits a strong positive effect, highlighting the enduring relevance of older books when reintroduced to the market.
+The number of pages shows a moderate positive effect, suggesting that longer books may appeal to certain segments of readers, while cover type demonstrates variability in its impact.
+For example, "Board Books" have a distinct positive association with higher rating counts, likely reflecting their suitability for specific demographics, such as young children or educational purposes.
+Overall, these findings provide a nuanced understanding of the interplay between physical, temporal, and audience-related factors in shaping the popularity of children’s books.
 
-## Implication and Significance
+The results underline the importance of examining a broader range of variables when predicting book popularity.
+While audience reception, measured through average ratings, remains a dominant factor, the study reveals that physical and temporal attributes also play significant roles.
+This expanded perspective challenges conventional notions that prioritize user preferences alone and introduces new dimensions for publishers to consider.
+For instance, republish length's positive relationship with popularity underscores the potential for publishers to strategically republish older books to capture renewed interest, especially in niche or underserved markets.
+Similarly, the moderate effect of the number of pages suggests that the book's length may influence its perceived value or suitability for specific purposes, such as educational or leisure reading.
+These insights highlight the multifaceted nature of book popularity and provide a foundation for evidence-based decision-making in the publishing industry.
 
-Traditionally, the primary driver of a book's popularity is thought to be audience reception and average ratings (@loh2019d).
-However, this research challenges that conventional view by highlighting the influence of physical and temporal attributes.
-The findings suggest that the number of pages, a physical characteristic often overlooked, plays a meaningful role in predicting popularity.
-This insight provides publishers with an actionable metric—adjusting the length of books based on market trends and reader preferences could enhance engagement.
-Furthermore, the positive relationship between republish length and popularity emphasizes the potential of older books to regain market relevance through republication.
-This finding is particularly significant for publishers seeking to maximize revenue from their backlist by identifying and republishing titles with enduring appeal.
-Additionally, while cover type showed variability in its effects, physical formats like "Board Books" appear to hold distinct advantages in engaging readers, suggesting opportunities for targeted marketing of specific cover types.
+## Implication and significance
 
-## Research Limitation
+Traditionally, book publishers and marketers have focused on audience reception, primarily measured through average ratings, as the key driver of popularity and market success (@loh2019d).
+This research challenges this singular focus by demonstrating that physical and temporal attributes of books also significantly influence reader engagement and popularity.
+One of the most notable findings is the positive association between the number of pages and the popularity of children’s books.
+While it may seem intuitive that longer books offer more content and therefore more perceived value, this study confirms that length is a measurable and actionable attribute that can influence popularity.
+This insight is especially valuable for publishers designing books for different reader demographics, as it suggests that optimal page lengths can be tailored to target audiences to maximize engagement.
+For example, longer books may appeal to older children or those seeking more immersive reading experiences, whereas shorter books may be more suitable for younger audiences.
 
-Despite the insights gained, the research has notable limitations, primarily stemming from the dataset's scope and quality.
-The GLM model developed for this study showed modest predictive power, indicating that other significant predictors of book popularity remain unexamined.
-Variables such as genre and target audience demographics, which could provide critical context for understanding engagement, were absent from the dataset.
-Additionally, the dataset contained continuous variables with a high prevalence of outliers, which were retained to avoid data loss given the limited sample size.
-This decision may have affected model accuracy and generalizability.
-Moreover, the assumption of independence between observations may not fully capture complex market dynamics, such as interdependencies among books within a series or franchise.
+Another critical finding is the strong positive relationship between republish length and popularity.
+This suggests that older books, when republished, have the potential to regain or even surpass their original popularity.
+This result is particularly significant for publishers looking to maximize the value of their backlist, as it highlights the opportunity to reintroduce older titles to new generations of readers.
+This finding aligns with broader trends in the publishing industry, where nostalgia and the rediscovery of classic books often drive market success.
+Additionally, the variability in the impact of cover types reveals opportunities for targeted marketing.
+For instance, "Board Books" show a distinct advantage in terms of popularity, likely due to their durability and suitability for young children.
+Publishers can leverage this knowledge to market specific formats to the appropriate audience, enhancing both reader satisfaction and sales performance.
+Overall, the findings provide a more comprehensive understanding of the factors driving children’s book popularity and offer actionable insights for publishers, marketers, and authors.
 
-## Conclusive Statement and Future Research
+# Research limitation
 
-This study concludes that children’s book popularity is influenced not only by audience ratings but also by physical attributes such as the number of pages and temporal factors like republish length.
-Publishers can leverage these findings to make strategic decisions, such as optimizing book lengths and capitalizing on the market potential of older, republished books.
-However, the limitations of the current model underscore the need for further research.
-Future studies should include variables such as genre, target audience, and marketing efforts to enhance predictive accuracy and provide a more comprehensive understanding of popularity drivers.
-Addressing outliers and applying advanced machine learning techniques, such as neural networks or ensemble methods, could improve model robustness and predictive capability.
-Additionally, incorporating cross-validation approaches would ensure that future models are better generalized to real-world data, paving the way for more effective predictions and actionable insights in the publishing industry.
+Despite its contributions, this study has several limitations that warrant careful consideration.
+First, the dataset's scope and quality impose constraints on the analysis.
+While the GLM model used in this study identifies significant predictors, its overall predictive power is modest, suggesting that additional variables not included in the dataset could play a critical role in determining book popularity.
+For instance, variables such as genre and target audience demographics were absent, yet these factors are likely to have substantial effects on engagement levels.
+Including these variables in future studies could significantly improve model accuracy and provide a more nuanced understanding of the factors influencing popularity.
+Furthermore, the dataset contains continuous variables with a high prevalence of outliers, which were retained to avoid data loss given the limited sample size.
+While this decision preserves the dataset's integrity, it may also affect the model's accuracy and generalizability, as extreme values can disproportionately influence regression coefficients.
+
+Another limitation lies in the assumption of independence between observations, which may not fully capture the complex market dynamics of book publishing.
+For example, books within the same series or franchise are likely to have interdependent popularity metrics due to shared branding, characters, or themes.
+Ignoring these interdependencies may lead to an oversimplification of the factors driving engagement.
+Additionally, the dataset does not account for external factors such as marketing efforts, seasonal trends, or the influence of awards and critical reviews, all of which could significantly impact book popularity.
+Addressing these limitations in future research could provide a more comprehensive and accurate understanding of the drivers of popularity, enabling publishers to make more informed decisions.
+
+## Conclusive statement and future research
+
+This study concludes that children’s book popularity is influenced by a combination of audience reception, physical attributes, and temporal factors.
+While average ratings remain a dominant predictor, attributes such as the number of pages and republish length also play significant roles in shaping reader engagement.
+These findings offer valuable insights for publishers seeking to optimize their strategies.
+For example, adjusting book lengths to align with market trends and reader preferences could enhance engagement, while strategically republishing older titles could capitalize on their enduring appeal.
+However, the study's limitations highlight the need for further research to build on these insights.
+Future studies should incorporate additional variables, such as genre, target audience, and marketing efforts, to provide a more holistic understanding of popularity drivers.
+Addressing outliers through robust statistical methods and applying advanced machine learning techniques, such as neural networks or ensemble methods, could improve model robustness and predictive capability.
+
+Moreover, incorporating cross-validation approaches would ensure that future models are better generalized to real-world data, enhancing their applicability in practical settings.
+Future research could also explore the interactions between variables, such as how genre and cover type jointly influence popularity, to uncover deeper insights.
+Expanding the dataset to include international books and broader demographic information could further enrich the analysis and make the findings more generalizable.
+By addressing these gaps, future studies can provide more accurate predictions and actionable recommendations, ultimately benefiting publishers, authors, and readers alike.
+These advancements would not only improve the predictive power of models but also deepen our understanding of the multifaceted factors driving children’s book popularity in a rapidly evolving market.
 

### 2024-12-02 scripts/06-model_data.R

@@ -52,26 +52,45 @@ plot_model <- ggplot(model_summary, aes(x = term, y = estimate)) +
   theme_minimal()
 plot_model
 
-# Predicted values 
-glm_predictions <- predict(glm_model, type = "response")
-lm_predictions <- predict(lm_model, type = "response")
 
-# Observed values
-observed_values <- analysis_data$rating_count
+#### Model comparison and evaluation ####
+# Split Data into Train and Test Sets 
+set.seed(123)  # For reproducibility
+train_indices <- sample(1:nrow(analysis_data), size = 0.8 * nrow(analysis_data))
+train_data <- analysis_data[train_indices, ]
+test_data <- analysis_data[-train_indices, ]
 
-# MSE Calculation
+# Fit GLM model on training data
+glm_model <- glm(rating_count ~ publish_year + republish_length + pages + as.factor(cover) + rating,
+                 family = poisson(link = "log"), data = train_data)
+
+# Fit LM model on training data
+lm_model <- glm(rating_count ~ publish_year + republish_length + pages + as.factor(cover) + rating,
+                data = train_data)
+
+#### Model Analysis on Test Set ####
+# Predicted values for the test set
+glm_predictions <- predict(glm_model, newdata = test_data, type = "response")
+lm_predictions <- predict(lm_model, newdata = test_data, type = "response")
+
+# Observed values in the test set
+observed_values <- test_data$rating_count
+
+# MSE Calculation for the test set
 glm_mse <- mean((observed_values - glm_predictions)^2)
 lm_mse <- mean((observed_values - lm_predictions)^2)
 
-# RMSE Calculation
+# RMSE Calculation for the test set
 glm_rmse <- sqrt(glm_mse)
 lm_rmse <- sqrt(lm_mse)
 
-# Output MSE and RMSE for both models
-cat("GLM Model MSE:", glm_mse, "\n")
-cat("GLM Model RMSE:", glm_rmse, "\n")
-cat("LM Model MSE:", lm_mse, "\n")
-cat("LM Model RMSE:", lm_rmse, "\n")
+# Output MSE and RMSE for test set
+cat("GLM Model MSE (Test Set):", glm_mse, "\n")
+cat("GLM Model RMSE (Test Set):", glm_rmse, "\n")
+cat("LM Model MSE (Test Set):", lm_mse, "\n")
+cat("LM Model RMSE (Test Set):", lm_rmse, "\n")
+
+
 
[…]
